### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/AP_Association.tex
update

% AP Association
\section{Problem and Algorithm}
	In a WLAN with multiple APs, each user needs to decide which AP he would like to associate with before starting to transmit or receive data. In other words, we perform AP association before we perform bandwidth allocation. Therefore, we consider an AP association problem that we assign each user to an AP and perform bandwidth allocation such that the allocated bandwidth to each user is under proportional fairness.

	In this AP association problem AAPFM, there are $m$ APs and $n$ users in a network supporting MU-MIMO. On each AP $i$ and user $j$, there are $l_i$ and $c_j$ antennas respectively. We assume all neighbor APs of each AP $i$ are set on the different channel, so they have no inter-interference. During each unit time, each user can associate with exact one AP. After user $j$ has associated with AP $i$, AP $i$ can communicate to user $j$ with at most $c_j$ antennas simultaneously by using beamforming in the downlink. We would like to allocate the bandwidth to each user under proportional fairness. In other words, we maximize the sum of the utility function of each user's allocated bandwidth. After solving the optimization problem, we obtain the receiving time corresponding to the antenna on the AP and the user. Then we schedule the receiving time of each user to corresponding antennas on the associated AP.

	Our problem AAPFM can be formulated as follows:

	\begin{equation}
		\begin{aligned}
			& \text{maximize} 
			& & \sum_{j \in U} \log (b_{j}) \\
			& \text{subject to} 
			& & b_{j} = \sum_{i \in A} x_{ij} \sum_{k \in T_{i}} r_{ikj} t_{ikj}, & & \forall j \in U, \\
			& & & \sum_{i \in A} x_{ij} = 1, & & \forall j \in U, \\
			& & & \sum_{i \in A} x_{ij} \sum_{k \in T_i } t_{ikj} \le c_j, & & \forall j \in U, \\
			& & & \sum_{j\in U} t_{ikj} \le 1, & & \forall i \in A, k \in T_i,  \\
			& & & 0 \le t_{ikj} \le 1, & & \forall i \in A, k \in T_i, j \in U, \\
			& & & x_{ij} = \{0, 1\}, & & \forall i \in A, j \in U. \\
		\end{aligned}
	\end{equation}

	In this non-linear program, $x_{ij}$ denotes whether user $j$ associates with AP $i$ or not. The first constraint shows the bandwidth allocated to user $j$ equals to the sum of the bit rate of the link between the antenna on the associated AP $i$ and user $j$ multiplying the receiving time solved by our algorithm. The second constraint specifies each user $j$ should associate with exact one AP. The third constraint specifies the total receiving time of user $j$ is no more than the number of antennas on user $j$. The forth constraint means the total transmission time of antenna $k$ on AP $i$ is no more than the unit time. So, the transmission time from antenna $k$ on AP $i$ to user $j$ is also no more than the unit time and not less than zero.

	Then, we relax the program by letting $0 \le x_{ij} \le 1$, $p_{ikj} = x_{ij} t_{ikj}$, $p_{ikj} \ge 0$, and $\sum_{j \in U} p_{ikj} \le 1$. The non-linear program relaxation as follows:

	\begin{equation} \label{eq:cvxpr}
		\begin{aligned}
			& \text{maximize} 
			& & \sum_{j \in U} \log (b_{j}) \\
			& \text{subject to} 
			& & b_{j} = \sum_{i \in A} \sum_{k \in T_{i}} r_{ikj} p_{ikj}, & & \forall j \in U, \\
			& & & \sum_{i \in A} \sum_{k \in T_i } p_{ikj} \le c_j, & & \forall j \in U, \\
			& & & \sum_{j\in U} p_{ikj} \le 1, & & \forall i \in A, k \in T_i,  \\
			& & & p_{ikj} \ge 0, & & \forall i \in A, k \in T_i, j \in U. \\
		\end{aligned}
	\end{equation}

	This program is a convex program and we can use interior-point method to solve it in polynomial time \cite{boyd2004convex}. Thus, we obtain $p_{ikj}^{*}$. We know $b_j^* = \sum_{i \in A} \sum_{k \in T_{i}} r_{ikj} p_{ikj}^* = \sum_{i \in A} b_{ij}^*, \forall j \in U$. So we can obtain $b_{ij}^* = \sum_{k \in T_{i}} r_{ikj} p_{ikj}^*, \forall i \in A, j \in U$. For each user $j$, in order to decide which $x_{ij}$ to be $1$, we choose the AP $i$ whose $b_{ij}$ is maximum and set $x_{ij} = 1$. Otherwise, $x_{ij} = 0$. The algorithm is shown in Algorithm 1.

	After we decide each user associate with which AP, for each AP, we perform the bandwidth allocation algorithm (Algorithm 2) to obtain the receiving time of each user.

%	Finally, we can obtain the value of the sum of the utility function.

	\begin{equation} \label{eq:cvxp}
		\begin{aligned}
			& \text{maximize} 
			& & \sum_{j \in U_i} \log (b_{j}) \\
			& \text{subject to} 
			& & b_{j} = \sum_{k \in T_{i}} r_{ikj} t_{ikj}, & & \forall j \in U_i, \\
			& & & \sum_{k \in T_i } t_{ikj} \le c_j, & & \forall j \in U_i, \\
			& & & \sum_{j\in U} t_{ikj} \le 1, & & \forall k \in T_i,  \\
			& & & t_{ikj} \ge 0, & & \forall k \in T_i, j \in U_i. \\
		\end{aligned}
	\end{equation}

	 Then, we perform Time Slot Scheduling Algorithm (Algorithm 3) to schedule each user on the corresponding antennas on the AP.

%	we propose a heuristic algorithm to solve it. In first stage, we associate each MD to an AP which allocates the maximal bandwidth to it sequentially. For MD $i$, we let $A_i$ denote the set of APs such that MD $i$ is in the coverage areas of these APs. There may be some MDs that have already been associated with these APs in $A_i$. MD $i$ will be associated with each AP in $A_i$ temporary and use the interior-point method for the bandwidth allocation problem to obtain allocated bandwidth of each association. Then MD $i$ selects the AP which allocates maximal bandwidth to it to associate with.

%	In second stage, after all MDs have been associated with APs, for each AP, we use the bandwidth allocation algorithm to obtain the receiving time and the allocated bandwidth of each MD associated with the AP. We sum the throughput of all MDs to obtain the total throughput. Then we schedule the receiving time of each MD to the time slots of antennas on APs.

	For each kind of AP  association there exists a kind of bandwidth allocation such that the sum of the utility function is maximal in that AP association. In other words, for each kind of AP association there exists corresponding proportional fairness respectively. The goal of our algorithm is to find a kind of AP association such that the sum of the utility function is maximum in AAPFM.

	We can think the utility function of each user's allocated bandwidth as the satisfaction corresponding to allocated bandwidth for each user. While we maximize the sum of the utility function, we maximize the total satisfaction. When the total satisfaction is maximum, it attains some fairness criterion. Before we solve the optimization problem, we need to choose a utility function that can represent the satisfaction of the user in the problem. In some papers, they think the utility function is a strict concave function when we consider a problem about networks because we think that the satisfaction of the user is decrease margin. If we let the utility function be logarithm, when sum of the utility function is maximum, we call the allocated bandwidth is in proportional fairness.

	If the solution of our algorithm CVXP is not an optimal solution, what is the meaning to compare the solution with another solution which is also not an optimal solution. We can think we compare these kinds of AP association to each other and find one kind such that the total satisfaction corresponding to the allocated bandwidth is maximum among them. Then, the total satisfaction is close to the optimal solution.

	\begin{algorithm}[t] 
		\label{algo:apassociation}
		\small { 
			\caption{AP Association} 
			\algsetup{linenosize=\small, linenodelimiter=.} 
			\begin{algorithmic}[1] 
				\REQUIRE {$A$: a set of APs, $\{T_i|\forall i \in A\}$ where $T_i$: a set of antennas on AP $i$, $U$: a set of users, and the bit rate table $\{r_{ikj}|\forall i \in A, k \in T_i, j \in U \}$} 
				\STATE Solve the convex program (\ref{eq:cvxpr}), get the optimal solution $(b^*,p^*)$
				\FOR {$j$ := 1 \TO $|U|$}
					\STATE $i' \gets 1$
					\STATE $b_{i'j} \gets 0$
					\FOR {$i$ := 1 \TO $|A|$}
						\STATE $b_{ij} \gets 0$.
						\FOR {$k$ := 1 \TO $|T_{i}|$}
							\STATE $b_{ij} \gets b_{ij} + r_{ikj}p_{ikj}^*$
						\ENDFOR
						\IF {$b_{ij} > b_{i'j}$}
							\STATE $i' \gets i$
							\STATE $b_{i'j} \gets b_{ij}$
						\ENDIF
					\ENDFOR
					\FOR {$i$ := 1 \TO $|A|$}
						\IF {$i = i'$}
							\STATE $x_{ij} \gets 1$
						\ELSE
							\STATE $x_{ij} \gets 0$
						\ENDIF
					\ENDFOR
				\ENDFOR
				\STATE Return $x \gets [x_{ij}|\forall i \in A, \forall j \in U ]$.
			\end{algorithmic} 
		}
	\end{algorithm}

	\begin{algorithm}[t] 
		\label{algo:bandalloc}
		\small { 
			\caption{Bandwidth Allocation} 
			\algsetup{linenosize=\small, linenodelimiter=.} 
			\begin{algorithmic}[1] 
				\REQUIRE {$A$: a set of APs, $\{T_i|\forall i \in A\}$ where $T_i$: a set of antennas on AP $i$, $U$: a set of users, $x$: an association matrix, and the bit rate table $\{r_{ikj}|\forall i \in A, k \in T_i, j \in U \}$}
				\FOR {$i$ := 1 \TO $|A|$}
					\STATE $U_i \gets \{j|x_{ij} = 1, \forall j \in U \}$
					\STATE Solve the convex program (\ref{eq:cvxp}), get optimal solution $(b^*,t^*)$
				\ENDFOR
				\STATE Return $t \gets \{t_{ikj}^*|\forall i \in A, k \in T_i, j \in U \}, b \gets \{b_j^* |\forall j \in U \}$.
			\end{algorithmic} 
		}
	\end{algorithm}

	\begin{algorithm}[t] 
		\label{algo:timesched}
		\small { 
			\caption{Time Slot Scheduling} 
			\algsetup{linenosize=\small, linenodelimiter=.} 
			\begin{algorithmic}[1] 
				\REQUIRE {$A$: a set of APs, $\{T_i|\forall i \in A\}$ where $T_i$: a set of antennas on AP $i$, $U$: a set of users, $\{t_{ikj}|\forall i \in A, k \in T_i, j \in U\}$ where $t_{ikj}$: receiving time slots}
				\FOR {$i$ := 1 \TO $|A|$}
					\FOR {$k$ := 1 \TO $|T_i|$}
						\FOR {$t$ := 1 \TO $1000$}
							\STATE $ts_{ikt} \gets 0$
						\ENDFOR
					\ENDFOR
				\ENDFOR
				\FOR {$i$ := 1 \TO $|A|$}
					\FOR {$k$ := 1 \TO $|T_i|$}
						\FOR {$j$ := 1 \TO $U$}
							\STATE $t \gets 0$
							\STATE $tsNeed_{ikj} \gets t_{ikj} $
%							\STATE Schedule $P_{j}$ on time slots of corresponding antennas.
							\FOR {$l$ := 1 \TO $tsNeed_{ikj}$}
								\WHILE {$1$}
									\IF {$ts_{ikt}$ is occupied}
										\STATE $t \gets t+1$
										\STATE continue
									\ENDIF
									\STATE $overlapped \gets 0$
									\FOR {$k'$ := $1$ \TO $|T_i|$}
										\IF {$ts_{ik't} = j$}
											\STATE $overlapped \gets overlapped + 1$
										\ENDIF
									\ENDFOR
									\IF {$overlapped < c_j$}
										\STATE $ts_{ikt} \gets j$
										\STATE $t \gets t+1$
										\STATE break
									\ELSE
										\STATE $t \gets t+1$
										\STATE continue									
									\ENDIF
								\ENDWHILE
							\ENDFOR
						\ENDFOR
					\ENDFOR
				\ENDFOR
				\STATE Return $ts \gets \{ts_{ikt}|\forall i \in A, k \in T_i, j \in \{1,...,1000\} \}$.
			\end{algorithmic} 
		}
	\end{algorithm}	
%	\begin{algorithm}[t] 
%		\small { 
%			\caption{AP Association and Bandwidth Allocation} 
%			\algsetup{linenosize=\small, linenodelimiter=.} 
%			\begin{algorithmic}[1] 
%				\REQUIRE {A set of APs $A$, a set of antennas $T_{i}$ on AP $i$, $\forall i \in A$, and a set of mobile devices $U$} 
%				\STATE Calculate the data rate $r_{ikj}$ between antenna $k$ on AP $i$ and MD $j$ according to the power of antenna $k$ and the distance between AP $i$ and MD $j$.
%				\STATE The data rate table $R$ is composed of $r_{ikj}, \forall i \in A, k \in T_{i}, j \in U$; 
%				\FOR {$j \in U$}
%				\STATE $A_j \gets$ the set of APs of which $j$ is in the coverage areas
%				\FOR {$i \in A_j$}
%				\STATE $U_{i} \gets$ the set of MDs associated with AP $i$.
%				\STATE $U_{i} \gets$ $U_{i} \cap \{j\}$
%				\STATE $P \gets$ interior-point method $(T_{i},U_{i})$.
%				\STATE $P_{j} \gets$ element $j$ in $P$.
%				\STATE $BW_{ij} \gets$ the temporary allocated bandwidth from $i$ derive by $R$ and $P_{j}$.
%				\STATE $U_{i} \gets$ $U_{i} \setminus \{j\}$
%				\ENDFOR
%				\STATE Select AP $i$ to be associated with such that $BW_{ij}$ is maximum in $BW_{j}=\{BW_{1j},...,BW_{|A_{j}|j}\}$.
%				\ENDFOR
%				\FOR {$i \in A$}
				%    \STATE $T_i \gets$ the set of antennas on $i$
%				\STATE $U_i \gets$ the set of MDs associated with AP $i$.
%				\STATE $P_{i} \gets$ interior-point $(T_{i},U_{i})$.
				%    \STATE $throughput[i] \gets$ the throughput computed by algo. 1
%				\FOR {$j \in U_i$}
%				\STATE $P_{j} \gets$ element $j$ in $P_{i}$.
%				\STATE Calculate $BW_{ij}$ from $R, T_{i}, P_{j}$.
%				\ENDFOR
%				\ENDFOR
%				\STATE Return $P \gets \{P_{1},...,P_{|A|}\}$.
%			\end{algorithmic} 
%		}
%	\end{algorithm}

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/AP_Association_Analysis.tex
update

% AP Association Analysis
\section{Analysis}
	After solving the convex program, we can obtain $b_j^* = \sum_{i \in A} b_{ij}^*, \forall j \in U.$
	For each user $j$, we associate user $j$ with AP $i'$ such that $b_{i'j}^*$ is maximum in $\{b_{ij}^*|\forall i \in A \}.$ 
	Let $$\hat{b}_j = b_{i'j}^*, \forall j \in U.$$
	Then, $$\hat{b}_j \ge \frac{b_j^*}{|A|}.$$
	We know $$\sum_{j \in U} \log{b_j} = \sum_{i \in A} \sum_{j \in U_i} \log{b_j} \ge \sum_{i \in A} \sum_{j \in U_i} \log{\hat{b}_j} = \sum_{j \in U} \log{\hat{b}_j}.$$
	Then, $$\sum_{j \in U} \log{\hat{b}_j} \ge \sum_{j \in U} \log{\frac{b_j^*}{|A|}} $$ $$ = \sum_{j \in U} (\log{b_j^*}-\log{|A|}) = \sum_{j \in U} \log{b_j^*} - |U|\log{|A|} \ge OPT - |U|\log{|A|}.$$

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/AP_Assoication_for_Proportional_Fairness_in_MU-MIMO_Multi-rate_WLANs.tex
update

%
\documentclass[a4paper, 12pt]{report}
% packages
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{algorithm} 
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[toc]{appendix}
% style
\topmargin 0cm \oddsidemargin 0.5cm \headsep 1.5cm \headheight 0.5cm
\textheight 21.5cm \textwidth 15.2cm \marginparwidth 0.5cm
\marginparsep 0cm
\floatsep 0.8cm     %頁之上端與下端圖表與圖表之間的間距
\textfloatsep 0.8cm %頁之上端與下端圖表與文字之間的間距
\intextsep 1.0cm    %指定為 h 的圖表與文字之間的間距
% new command
\newcommand{\doublespace}{\addtolength{\baselineskip}{.6\baselineskip}}

% title and author
\title{AP Association for Proportional Fairness in MU-MIMO Multi-rate WLANs}
\author{YuShu Chen}
%
\begin{document}
	\begin{titlepage}
%		\maketitle
		\begin{center}
			%\vspace{2.5cm}
			\Large{\bf{AP Association for Proportional Fairness in MU-MIMO Multi-rate WLANs\\}}
			\vspace{3cm}
			Department of Computer Science\\
			National Tsing Hua University\\
			\vspace{2cm}
			%(Draft)\\
			\vspace{4.5cm}
			\parbox[t]{7cm}{
				%實際寬度自行再調整
				Advisor: Dr. Ming-Jer~Tsai\\
				Student: Yu-Shu~Chen\\
			} \\
			\vspace{5cm}
			July 2015\\
		\end{center}
	\end{titlepage}
	\pagenumbering{roman}
	\doublespace
	\chapter*{Abstract}
		\input{Abstract.tex}
	% table of content
	\addcontentsline{toc}{chapter}{Contents}
	\tableofcontents
	\cleardoublepage

	\addcontentsline{toc}{chapter}{List of Figures}
	\listoffigures
	\cleardoublepage

	\addcontentsline{toc}{chapter}{List of Tables}
	\listoftables
	\cleardoublepage

	\pagenumbering{arabic}
	\chapter{Introduction and Related Work}
		In this chapter, we introduce the AP association problem in addition to background knowledge and show the related work.
		\input{Introduction.tex}
		\input{Related_Work.tex}
	\chapter{Bandwidth Allocation}
		In this chapter, we describe how to allocate bandwidth for proportional fairness to each user associating with the same AP.
		\input{Bandwidth_Allocation.tex}
	\chapter{AP Association}
		In this chapter, we describe the AP association problem AAPFM and propose an algorithm called CVXP to solve it. We will analysis CVXP and show the hardness of this problem.
		\input{AP_Association.tex}
		\input{AP_Association_Analysis.tex}
		\input{AP_Association_Hardness.tex}
	\chapter{Performance Evaluations}
		In this chapter, we build a bit rate table for simulations and compare the result of our algorithms CVXP to a naive algorithm HDR in each simulation.
		\input{Bit_Rate_Table.tex}
%		\input{Evaluation_for_AP_Association.tex}
		\input{Evaluation_for_AP_Association_2.tex}
	\chapter{Conclusion}
		\input{Conclusion.tex}
%	\input{Bibliography.tex}
	\bibliographystyle{IEEEtran}
	\bibliography{references}
	\begin{appendices}
		\chapter{Details of Simulations}
		\label{apendix:dos}
		\input{Details_of_Simulations}
	\end{appendices}
\end{document}

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Abstract.tex
update

% Abstract
Design of AP association algorithms has received considerable attentions in wireless local area networks (WLANs) because the  bandwidth allocated to users is decided by the AP association algorithms designed. In order to make the allocated bandwidth of each user satisfy the lower bound of the requirement of each user, AP association needs to be considered about fairness. The existing algorithms concerning the total bandwidth optimization problem under fairness constraints only allow each AP to be able to communicate with at most one user in a time slot. However, today, by the beamforming technique makes it possible that each AP with multiple antennas can transmit data to multiple users simultaneously.

In this thesis, we study the AP association for proportional fairness, termed AAPFM, to maximize the sum of the utility function of the bandwidth allocated to each user in MU-MIMO WLANs. To the best of our knowledge, we are first to study the AP association problem for proportional fairness in MU-MIMO WLANs. In this thesis, we show the AAPFM problem is NP-hard and propose an approximation algorithm that the solution is greater than $OPT - |U|\log{|A|}$ where $U$ is the set of users and $A$ is the set of APs.

Simulations for evaluations show that the proposed AP association algorithm has good performance in terms of the sum of the utility function of the bandwidth allocated to each user.

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Abstract_chinese.tex
update

% 中文摘要

在無線區域網路裡無線網路基地台連接配對問題的演算法設計已經受到許多人的關注，這是因為分配給使用者的頻寬會隨著演算法的不同而有差別。為了要讓每個使用者所被分配到的頻寬能夠符合他的最低需求，在無線網路基地台連接配對問題需要去考慮公平性。已經存在的演算法只有考慮在每個無線網路基地台在某個時間點只能跟一個使用者溝通的環境下，去達到頻寬分配公平性最佳化的狀態。然後現在藉著使用波束成型技術可以讓有多根天線的無線網路基地台能夠同時跟多位使用者傳遞資料。

在這篇論文中，我們探討在多用戶多輸入多輸出的無線區域網路環境下，達成比例公平分配條件的無線網路基地台連接配對問題來使得分配給使用者頻寬的效用函數的和最大化。就我們所知，我們是第一個來探討這個問題的。在這篇論文中，我們會證明這是一個NP-hard 的問題並且提出一個近似演算法使得它的答案會不小於$OPT - |U|\log(|A|)$，在這裡U 是使用者的集合，A 是無線網路基地台的集合。

從模擬的結果可以看出我們所提出的演算法對於分配給使用者頻寬的效用函數的和有良好的表現。

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Bandwidth_Allocation.tex
update

% Bandwidth Allocation
\section{Problem and Algorithm}
	In a WLAN, each user needs to be allocated bandwidth to transmit or receive data. The bandwidth of a user in the downlink is the number of total receiving bits in one second. The bandwidth $b_j$ can be formulated as $b_j = \sum_{i} r_{ij} \times t_{ij}$, where $r_{ij}$ is the bit rate, $t_{ij}$ is the receiving time, and $ 0 \le t_{ij} \le 1$. The central controller of APs schedules the communication time of each user associated with some AP under certain fairness criterion. The amount of allocated bandwidth for each user varies according to different fairness criterions. The figure \ref{figure:exp03_a_b} shows the distribution of sorted allocated bandwidth in non-decreasing order under some fairness criterions like maximizing total bandwidth (no fairness), proportional fairness, time-based fairness, and bandwidth-based fairness. We can observe that fairness and total bandwidth are trade-off.

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp03_allocated_bandwidth.eps}
				\caption{The distribution of sorted allocated bandwidth in non-decreasing order.}
				\label{figure:exp03_a_b}
			\end{center}
		\end{figure}

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp03_allocated_bandwidth_zoom_in.eps}
				\caption{The detail of the distribution of sorted allocated bandwidth.}
				\label{figure:exp03_a_b_z_i}
			\end{center}
		\end{figure}

	In this thesis, we enforce the proportional fairness to bandwidth allocation because it has been in some recent standards (e.g., WiMAX, LTE). The definition of the proportional fairness is that if the allocation $b^{*}=\{b_1^*,...,b_n^*\}$ is proportionally fair, then any other allocation $b = \{b_1,...,b_n\}$ will result in
	$$ \sum_{i = 1}^{n} \frac{b_i - b_i^*}{b_i^*} \le 0. $$
	The utility function for the proportional fairness is $\log(\cdot)$. we maximize the sum of the utility function to attain the proportional fairness condition.

	For bandwidth allocation in our problem, first, we consider a scenario that there is an AP with $l$ antennas in a network supporting MU-MIMO. There are $n$ users associating with the AP. For each user $i$, there are $c_i$ antennas on user $i$. When the AP would like to communicate to user $i$ in the downlink, the AP can use at most $c_i$ antennas to transmit data to user $i$ simultaneously. During each unit time, we would like to allocate the bandwidth to each user under proportional fairness condition. Then, according to the allocated bandwidth, we schedule the transmission time from each antenna on the AP to each user. We formulate our bandwidth allocation problem as follows:

	\begin{equation*}
		\begin{aligned}
			& \text{maximize} 
			& & \sum_{j \in U} \log ( b_{j} ) \\
			& \text{subject to} 
			& & b_{j} = \sum_{k \in T} r_{kj}p_{kj}, & & \forall j \in U,\\
			& & & \sum_{k\in T} p_{kj} \le c_{j}, & &  \forall j \in U, \\
			& & & \sum_{j\in U} p_{kj} \le 1, & & \forall k \in T,  \\
			& & & 0 \le p_{kj} \le 1, & & \forall k \in T, j \in U.
		\end{aligned}
	\end{equation*}

	The first constraint shows the bandwidth allocated to user $j$ equals to the sum of the bit rate of the link between the antenna  $k$ and user $j$ multiplying the receiving time $p_{kj}$ solved by our algorithm. The second constraint specifies the total receiving time of user $j$ is no more than the number of antennas on user $j$. The third constraint means the total transmission time of antenna $k$ on the AP is no more than the unit time. So, the transmission time from antenna $k$ on the AP to user $j$ is also no more than the unit time and not less than zero.

	The above program is a convex optimization problem because the sum of logarithm function is non-decreasing concave function and the constraints are all linear. We can use the interior-point method to solve it and obtain an optimal solution $p_{kj}^*$, $b_j^*$ in polynomial time \cite{boyd2004convex}. The allocated bandwidth corresponding to the solution $b_j^*$ is under the proportional fairness condition.

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Bibliography.tex
update

\begin{thebibliography}{10}
	\bibitem{li2002mimo}
	Y.~Li, J.~H. Winters, and N.~R. Sollenberger, ``Mimo-ofdm for wireless
	communications: signal detection with enhanced channel estimation,''
	\emph{Communications, IEEE Transactions on}, vol.~50, no.~9, pp. 1471--1477,
	2002.

	\bibitem{kelly1997charging}
	F.~Kelly, ``Charging and rate control for elastic traffic,'' \emph{European
		transactions on Telecommunications}, vol.~8, no.~1, pp. 33--37, 1997.

	\bibitem{li2008proportional}
	L.~Li, M.~Pal, and Y.~R. Yang, ``Proportional fairness in multi-rate wireless
	lans,'' in \emph{INFOCOM 2008. The 27th Conference on Computer
		Communications. IEEE}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 2008.

	\bibitem{li2014ap}
	W.~Li, S.~Wang, Y.~Cui, X.~Cheng, R.~Xin, M.~Al-Rodhaan, and A.~Al-Dhelaan,
	``Ap association for proportional fairness in multirate wlans,''
	\emph{Networking, IEEE/ACM Transactions on}, vol.~22, no.~1, pp. 191--202,
	2014.

	\bibitem{baid2012network}
	A.~Baid, M.~Schapira, I.~Seskar, J.~Rexford, and D.~Raychaudhuri, ``Network
	cooperation for client-ap association optimization,'' in \emph{Modeling and
		Optimization in Mobile, Ad Hoc and Wireless Networks (WiOpt), 2012 10th
		International Symposium on}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE,
	2012, pp. 431--436.

	\bibitem{karimi2014optimal}
	O.~B. Karimi, J.~Liu, and J.~Rexford, ``Optimal collaborative access point
	association in wireless networks,'' in \emph{INFOCOM, 2014 Proceedings
		IEEE}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 2014, pp. 1141--1149.

	\bibitem{gong2012ap}
	D.~Gong and Y.~Yang, ``Ap association in 802.11 n wlans with heterogeneous
	clients,'' in \emph{INFOCOM, 2012 Proceedings IEEE}.\hskip 1em plus 0.5em
	minus 0.4em\relax IEEE, 2012, pp. 1440--1448.

	\bibitem{yoon2013probeam}
	J.~Yoon, K.~Sundaresan, M.~A. Khojastepour, S.~Rangarajan, and S.~Banerjee,
	``Probeam: a practical multicell beamforming system for ofdma small-cell
	networks,'' in \emph{Proceedings of the fourteenth ACM international
		symposium on Mobile ad hoc networking and computing}.\hskip 1em plus 0.5em
	minus 0.4em\relax ACM, 2013, pp. 147--156.

	\bibitem{aryafar2010design}
	E.~Aryafar, N.~Anand, T.~Salonidis, and E.~W. Knightly, ``Design and
	experimental evaluation of multi-user beamforming in wireless lans,'' in
	\emph{Proceedings of the sixteenth annual international conference on Mobile
		computing and networking}.\hskip 1em plus 0.5em minus 0.4em\relax ACM, 2010,
	pp. 197--208.

	\bibitem{yoo2006optimality}
	T.~Yoo and A.~Goldsmith, ``On the optimality of multiantenna broadcast
	scheduling using zero-forcing beamforming,'' \emph{Selected Areas in
		Communications, IEEE Journal on}, vol.~24, no.~3, pp. 528--541, 2006.

	\bibitem{yoo2007multi}
	T.~Yoo, N.~Jindal, and A.~Goldsmith, ``Multi-antenna downlink channels with
	limited feedback and user selection,'' \emph{Selected Areas in
		Communications, IEEE Journal on}, vol.~25, no.~7, pp. 1478--1491, 2007.

	\bibitem{xie2014scalable}
	X.~Xie and X.~Zhang, ``Scalable user selection for mu-mimo networks,'' in
	\emph{INFOCOM, 2014 Proceedings IEEE}.\hskip 1em plus 0.5em minus 0.4em\relax
	IEEE, 2014, pp. 808--816.

	\bibitem{arslan2007channel}
	H.~Arslan \emph{et~al.}, ``Channel estimation for wireless ofdm systems,''
	\emph{IEEE Surveys and Tutorials}, vol.~9, no.~2, pp. 18--48, 2007.

	\bibitem{blough2014interference}
	D.~M. Blough, G.~Resta, and P.~Santi, ``Interference-aware proportional
	fairness for multi-rate wireless networks,'' in \emph{INFOCOM, 2014
		Proceedings IEEE}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 2014, pp.
	2733--2741.

	\bibitem{du2014ibeam}
	Y.~Du, E.~Aryafar, J.~Camp, and M.~Chiang, ``ibeam: Intelligent client-side
	multi-user beamforming in wireless networks,'' in \emph{INFOCOM, 2014
		Proceedings IEEE}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 2014, pp.
	817--825.

	\bibitem{wang2014simcast}
	G.~Wang, K.~Wu, Q.~Zhang, and L.~M. Ni, ``Simcast: Efficient video delivery in
	mu-mimo wlans,'' in \emph{INFOCOM, 2014 Proceedings IEEE}.\hskip 1em plus
	0.5em minus 0.4em\relax IEEE, 2014, pp. 2454--2462.

	\bibitem{yu2014combating}
	H.~Yu, O.~Bejarano, and L.~Zhong, ``Combating inter-cell interference in 802.11
	ac-based multi-user mimo networks,'' in \emph{Proceedings of the 20th annual
		international conference on Mobile computing and networking}.\hskip 1em plus
	0.5em minus 0.4em\relax ACM, 2014, pp. 141--152.

	\bibitem{boyd2004convex}
	S.~Boyd and L.~Vandenberghe, \emph{Convex optimization}.\hskip 1em plus 0.5em
	minus 0.4em\relax Cambridge university press, 2004.

\end{thebibliography}

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Bit_Rate_Table.tex
update

% Bit Rate Table
\section{Bit Rate Table}
	We build a bit rate table corresponding to the bit rate of the link between an antenna on an AP and a user derived from the transmission power of the antenna on the AP and the distance between the AP and the user, according to Shannon-Hartley theorem
	$$ C=B\log_2(1+S/N) $$
	where $C$ is the channel capacity in bps, $B$ is the bandwidth of the channel, and $S/N$ is the signal-to-noise ratio (SNR). The receiving power on the user is proportional to the transmit power and inversely proportional to the square of the distance. We set the bandwidth of each channel to $20 MHz$. Thus, the bit rate corresponding to the power and the distance is list in Table \ref{Tab:drol}.

	\begin{table} \small
		\centering \caption{User bit rate table}
		\renewcommand\arraystretch{1.0}
		\begin{tabular}{|c|c|c|} % m{5.38cm}
			\hline	Power (dBm) & Distance (m) & Bit rate (Mbps) \\
			\hline	$17$ & $\le 150$ & $6.5$ \\
			\hline	$17$ & $\le 100$ & $13$ \\		
			\hline	$17$ & $\le 85$ & $19.5$ \\
			\hline	$17$ & $\le 70$ & $26$ \\
			\hline	$17$ & $\le 55$ & $39$ \\
			\hline	$17$ & $\le 50$ & $52$ \\
			\hline	$17$ & $\le 45$ & $65$ \\
			\hline	$14$ & $\le 100$ & $6.5$ \\
			\hline	$14$ & $\le 70$ & $13$ \\
			\hline	$14$ & $\le 55$ & $19.5$ \\
			\hline	$14$ & $\le 50$ & $26$ \\
			\hline	$14$ & $\le 40$ & $39$ \\
			\hline	$14$ & $\le 35$ & $52$ \\
			\hline	$14$ & $\le 30$ & $65$ \\
			\hline	$11$ & $\le 70$ & $6.5$ \\
			\hline	$11$ & $\le 50$ & $13$ \\
			\hline	$11$ & $\le 40$ & $19.5$ \\
			\hline	$11$ & $\le 35$ & $26$ \\
			\hline	$11$ & $\le 30$ & $39$ \\
			\hline	$11$ & $\le 25$ & $52$ \\
			\hline	$11$ & $\le 20$ & $65$ \\
			\hline
		\end{tabular}\label{Tab:drol}
	\end{table}

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Conclusion.tex
update

% Conclusion
	AP association is an important problem for bandwidth allocation to each user under some fairness criterion in WLANs. In this thesis, we consider an AP association problem in MU-MIMO WLANs. Each AP with multiple antennas can transmit data to multiple users simultaneously in the downlink.
	To the best of our knowledge, we are first to introduce an AP association problem for proportional fairness in a MU-MIMO WLAN. The algorithms for AP association in SISO WLANs are not suitable for our problem because we need to decide which user uses which antennas on the AP.

	Our algorithm called CVXP is to formulate the problem into an integer program and relax it to a convex program. we solve the convex program in polynomial time and obtain the optimal fractional solution. According to the solution, we associate each user to the AP which allocate the maximum fractional bandwidth to the user. After AP association, for each AP, we allocate bandwidth to each user in the association set of users. We analyze our algorithm CVXP and make sure that the solution of CVXP is greater than $OPT - |U|\log{|A|}$ where $U$ is the set of users and $A$ is the set of APs.

%	The result of simulations will be depicted. T.B.D. for different distribution of positions of users and different number of antennas on users.

	We run 3 sets of simulations that the number of users is $225$, $441$, and $666$, respectively. We compare CVXP to a common algorithm called HDR which is to associate each user with the AP which gives the highest sum of the bit rate to the user. The result of simulations show CVXP outperforms HDR. In each simulation, the sum of the utility function of bandwidth allocated to the user from CVXP is greater than that from HDR. It means the bandwidth allocation from CVXP is closer to the proportional fairness criterion. The number of users who obtain more bandwidth from CVXP is greater than that from HDR.

%	The future work will be depicted. T.B.D.
	The lower bound of our algorithm depends on the number of users. In the future work, we would like to improve our lower bound by analyzing the fractional optimal solution and modifying the rounding algorithm.

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Details_of_Simulations.tex
update

% Details of Simulations

\subsubsection{SIMUL1-1-1}
	Fig. \ref{figure:simul1_1_1_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul1_1_1_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul1_1_1_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL1-1-2}
	Fig. \ref{figure:simul1_1_2_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul1_1_2_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul1_1_2_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL1-2-1}
	Fig. \ref{figure:simul1_2_1_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul1_2_1_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul1_2_1_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL1-2-2}
	Fig. \ref{figure:simul1_2_2_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul1_2_2_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul1_2_2_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL1-3-1}
	Fig. \ref{figure:simul1_3_1_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul1_3_1_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul1_3_1_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL1-3-2}
	Fig. \ref{figure:simul1_3_2_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul1_3_2_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul1_3_2_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL1-4}
	Fig. \ref{figure:simul1_4_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul1_4_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul1_4_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL2-1-1}
	Fig. \ref{figure:simul2_1_1_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul2_1_1_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul2_1_1_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL2-1-2}
	Fig. \ref{figure:simul2_1_2_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul2_1_2_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul2_1_2_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL2-2-1}
	Fig. \ref{figure:simul2_2_1_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul2_2_1_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul2_2_1_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL2-2-2}
	Fig. \ref{figure:simul2_2_2_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul2_2_2_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul2_2_2_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL2-3-1}
	Fig. \ref{figure:simul2_3_1_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul2_3_1_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul2_3_1_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL2-3-2}
	Fig. \ref{figure:simul2_3_2_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul2_3_2_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul2_3_2_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL2-4}
	Fig. \ref{figure:simul2_4_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul2_4_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul2_4_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL3-1-1}
	Fig. \ref{figure:simul3_1_1_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul3_1_1_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul3_1_1_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL3-1-2}
	Fig. \ref{figure:simul3_1_2_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul3_1_2_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul3_1_2_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL3-2-1}
	Fig. \ref{figure:simul3_2_1_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul3_2_1_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul3_2_1_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL3-2-2}
	Fig. \ref{figure:simul3_2_2_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul3_2_2_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul3_2_2_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL3-3-1}
	Fig. \ref{figure:simul3_3_1_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul3_3_1_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul3_3_1_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL3-3-2}
	Fig. \ref{figure:simul3_3_2_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul3_3_2_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul3_3_2_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

\subsubsection{SIMUL3-4}
	Fig. \ref{figure:simul3_4_p} shows $10$ patterns of the distribution of positions of users in simulation. Fig. \ref{figure:simul3_4_ba} shows the sorted bandwidth allocated to users. Fig. \ref{figure:simul3_4_u} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth between CVXP and HDR.

%=======
%\subsubsection{SIMUL1-1-1}
	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_01_position_v4.eps}
				\caption{pattern 1}
				\label{figure:simul1_1_1_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_02_position_v4.eps}
				\caption{pattern 2}
				\label{figure:simul1_1_1_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_03_position_v4.eps}
				\caption{pattern 3}
				\label{figure:simul1_1_1_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_04_position_v4.eps}
				\caption{pattern 4}
				\label{figure:simul1_1_1_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_05_position_v4.eps}
				\caption{pattern 5}
				\label{figure:simul1_1_1_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_06_position_v4.eps}
				\caption{pattern 6}
				\label{figure:simul1_1_1_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_07_position_v4.eps}
				\caption{pattern 7}
				\label{figure:simul1_1_1_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_08_position_v4.eps}
				\caption{pattern 8}
				\label{figure:simul1_1_1_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_09_position_v4.eps}
				\caption{pattern 9}
				\label{figure:simul1_1_1_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_10_position_v4.eps}
				\caption{pattern 10}
				\label{figure:simul1_1_1_j}
			\end{subfigure}
			\caption{Patterns of distribution of users in SIMUL1-1-1.}
			\label{figure:simul1_1_1_p}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul1_1_1_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul1_1_1_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul1_1_1_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul1_1_1_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul1_1_1_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul1_1_1_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul1_1_1_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul1_1_1_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul1_1_1_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp17_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul1_1_1_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL1-1-1.}
			\label{figure:simul1_1_1_ba}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=\textwidth]{fig/exp17_1-1-1_utility.eps}
				\caption{sum of utility function}
				\label{figure:simul1_1_1_u_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=\textwidth]{fig/exp17_1-1-1_bandwidth.eps}
				\caption{number of users}
				\label{figure:simul1_1_1_u_b}
			\end{subfigure}
			\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL1-1-1.}
			\label{figure:simul1_1_1_u}
		\end{center}
	\end{figure}

\clearpage

%\subsubsection{SIMUL1-1-2}
	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_01_position_v4.eps}
				\caption{pattern 1}
				\label{figure:simul1_1_2_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_02_position_v4.eps}
				\caption{pattern 2}
				\label{figure:simul1_1_2_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_03_position_v4.eps}
				\caption{pattern 3}
				\label{figure:simul1_1_2_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_04_position_v4.eps}
				\caption{pattern 4}
				\label{figure:simul1_1_2_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_05_position_v4.eps}
				\caption{pattern 5}
				\label{figure:simul1_1_2_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_06_position_v4.eps}
				\caption{pattern 6}
				\label{figure:simul1_1_2_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_07_position_v4.eps}
				\caption{pattern 7}
				\label{figure:simul1_1_2_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_08_position_v4.eps}
				\caption{pattern 8}
				\label{figure:simul1_1_2_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_09_position_v4.eps}
				\caption{pattern 9}
				\label{figure:simul1_1_2_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_10_position_v4.eps}
				\caption{pattern 10}
				\label{figure:simul1_1_2_j}
			\end{subfigure}
			\caption{Patterns of distribution of users in SIMUL1-1-2.}
			\label{figure:simul1_1_2_p}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul1_1_2_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul1_1_2_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul1_1_2_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul1_1_2_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul1_1_2_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul1_1_2_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul1_1_2_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul1_1_2_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul1_1_2_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp20_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul1_1_2_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL1-1-2.}
			\label{figure:simul1_1_2_ba}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp20_1-1-2_utility.eps}
				\caption{sum of utility function}
				\label{figure:simul1_1_2_u_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp20_1-1-2_bandwidth.eps}
				\caption{number of users}
				\label{figure:simul1_1_2_u_b}
			\end{subfigure}
			\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL1-1-2.}
			\label{figure:simul1_1_2_u}
		\end{center}
	\end{figure}

\clearpage

%\subsubsection{SIMUL1-2-1}
	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_01_position_v4.eps}
				\caption{pattern 1}
				\label{figure:simul1_2_1_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_02_position_v4.eps}
				\caption{pattern 2}
				\label{figure:simul1_2_1_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_03_position_v4.eps}
				\caption{pattern 3}
				\label{figure:simul1_2_1_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_04_position_v4.eps}
				\caption{pattern 4}
				\label{figure:simul1_2_1_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_05_position_v4.eps}
				\caption{pattern 5}
				\label{figure:simul1_2_1_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_06_position_v4.eps}
				\caption{pattern 6}
				\label{figure:simul1_2_1_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_07_position_v4.eps}
				\caption{pattern 7}
				\label{figure:simul1_2_1_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_08_position_v4.eps}
				\caption{pattern 8}
				\label{figure:simul1_2_1_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_09_position_v4.eps}
				\caption{pattern 9}
				\label{figure:simul1_2_1_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_10_position_v4.eps}
				\caption{pattern 10}
				\label{figure:simul1_2_1_j}
			\end{subfigure}
			\caption{Patterns of distribution of users in SIMUL1-2-1.}
			\label{figure:simul1_2_1_p}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul1_2_1_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul1_2_1_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul1_2_1_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul1_2_1_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul1_2_1_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul1_2_1_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul1_2_1_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul1_2_1_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul1_2_1_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp18_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul1_2_1_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL1-2-1.}
			\label{figure:simul1_2_1_ba}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp18_1-2-1_utility.eps}
				\caption{sum of utility function}
				\label{figure:simul1_2_1_u_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp18_1-2-1_bandwidth.eps}
				\caption{number of users}
				\label{figure:simul1_2_1_u_b}
			\end{subfigure}
			\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL1-2-1.}
			\label{figure:simul1_2_1_u}
		\end{center}
	\end{figure}

\clearpage

%\subsubsection{SIMUL1-2-2}
	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_01_position_v4.eps}
				\caption{pattern 1}
				\label{figure:simul1_2_2_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_02_position_v4.eps}
				\caption{pattern 2}
				\label{figure:simul1_2_2_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_03_position_v4.eps}
				\caption{pattern 3}
				\label{figure:simul1_2_2_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_04_position_v4.eps}
				\caption{pattern 4}
				\label{figure:simul1_2_2_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_05_position_v4.eps}
				\caption{pattern 5}
				\label{figure:simul1_2_2_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_06_position_v4.eps}
				\caption{pattern 6}
				\label{figure:simul1_2_2_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_07_position_v4.eps}
				\caption{pattern 7}
				\label{figure:simul1_2_2_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_08_position_v4.eps}
				\caption{pattern 8}
				\label{figure:simul1_2_2_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_09_position_v4.eps}
				\caption{pattern 9}
				\label{figure:simul1_2_2_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_10_position_v4.eps}
				\caption{pattern 10}
				\label{figure:simul1_2_2_j}
			\end{subfigure}
			\caption{Patterns of distribution of users in SIMUL1-2-2.}
			\label{figure:simul1_2_2_p}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul1_2_2_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul1_2_2_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul1_2_2_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul1_2_2_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul1_2_2_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul1_2_2_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul1_2_2_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul1_2_2_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul1_2_2_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp21_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul1_2_2_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL1-2-2.}
			\label{figure:simul1_2_2_ba}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp21_1-2-2_utility.eps}
				\caption{sum of utility function}
				\label{figure:simul1_2_2_u_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp21_1-2-2_bandwidth.eps}
				\caption{number of users}
				\label{figure:simul1_2_2_u_b}
			\end{subfigure}
			\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL1-2-2.}
			\label{figure:simul1_2_2_u}
		\end{center}
	\end{figure}

\clearpage

%\subsubsection{SIMUL1-3-1}
	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_01_position_v4.eps}
				\caption{pattern 1}
				\label{figure:simul1_3_1_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_02_position_v4.eps}
				\caption{pattern 2}
				\label{figure:simul1_3_1_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_03_position_v4.eps}
				\caption{pattern 3}
				\label{figure:simul1_3_1_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_04_position_v4.eps}
				\caption{pattern 4}
				\label{figure:simul1_3_1_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_05_position_v4.eps}
				\caption{pattern 5}
				\label{figure:simul1_3_1_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_06_position_v4.eps}
				\caption{pattern 6}
				\label{figure:simul1_3_1_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_07_position_v4.eps}
				\caption{pattern 7}
				\label{figure:simul1_3_1_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_08_position_v4.eps}
				\caption{pattern 8}
				\label{figure:simul1_3_1_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_09_position_v4.eps}
				\caption{pattern 9}
				\label{figure:simul1_3_1_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_10_position_v4.eps}
				\caption{pattern 10}
				\label{figure:simul1_3_1_j}
			\end{subfigure}
			\caption{Patterns of distribution of users in SIMUL1-3-1.}
			\label{figure:simul1_3_1_p}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul1_3_1_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul1_3_1_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul1_3_1_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul1_3_1_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul1_3_1_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul1_3_1_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul1_3_1_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul1_3_1_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul1_3_1_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp19_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul1_3_1_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL1-3-1.}
			\label{figure:simul1_3_1_ba}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp19_1-3-1_utility.eps}
				\caption{sum of utility function}
				\label{figure:simul1_3_1_u_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp19_1-3-1_bandwidth.eps}
				\caption{number of users}
				\label{figure:simul1_3_1_u_b}
			\end{subfigure}
			\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL1-3-1.}
			\label{figure:simul1_3_1_u}
		\end{center}
	\end{figure}

\clearpage

%\subsubsection{SIMUL1-3-2}
	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_01_position_v4.eps}
				\caption{pattern 1}
				\label{figure:simul1_3_2_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_02_position_v4.eps}
				\caption{pattern 2}
				\label{figure:simul1_3_2_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_03_position_v4.eps}
				\caption{pattern 3}
				\label{figure:simul1_3_2_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_04_position_v4.eps}
				\caption{pattern 4}
				\label{figure:simul1_3_2_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_05_position_v4.eps}
				\caption{pattern 5}
				\label{figure:simul1_3_2_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_06_position_v4.eps}
				\caption{pattern 6}
				\label{figure:simul1_3_2_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_07_position_v4.eps}
				\caption{pattern 7}
				\label{figure:simul1_3_2_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_08_position_v4.eps}
				\caption{pattern 8}
				\label{figure:simul1_3_2_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_09_position_v4.eps}
				\caption{pattern 9}
				\label{figure:simul1_3_2_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_10_position_v4.eps}
				\caption{pattern 10}
				\label{figure:simul1_3_2_j}
			\end{subfigure}
			\caption{Patterns of distribution of users in SIMUL1-3-2.}
			\label{figure:simul1_3_2_p}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul1_3_2_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul1_3_2_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul1_3_2_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul1_3_2_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul1_3_2_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul1_3_2_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul1_3_2_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul1_3_2_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul1_3_2_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp22_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul1_3_2_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL1-3-2.}
			\label{figure:simul1_3_2_ba}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp22_1-3-2_utility.eps}
				\caption{sum of utility function}
				\label{figure:simul1_3_2_u_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp22_1-3-2_bandwidth.eps}
				\caption{number of users}
				\label{figure:simul1_3_2_u_b}
			\end{subfigure}
			\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL1-3-2.}
			\label{figure:simul1_3_2_u}
		\end{center}
	\end{figure}

\clearpage

%\subsubsection{SIMUL1-4}
	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_01_position_v4.eps}
				\caption{pattern 1}
				\label{figure:simul1_4_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_02_position_v4.eps}
				\caption{pattern 2}
				\label{figure:simul1_4_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_03_position_v4.eps}
				\caption{pattern 3}
				\label{figure:simul1_4_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_04_position_v4.eps}
				\caption{pattern 4}
				\label{figure:simul1_4_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_05_position_v4.eps}
				\caption{pattern 5}
				\label{figure:simul1_4_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_06_position_v4.eps}
				\caption{pattern 6}
				\label{figure:simul1_4_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_07_position_v4.eps}
				\caption{pattern 7}
				\label{figure:simul1_4_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_08_position_v4.eps}
				\caption{pattern 8}
				\label{figure:simul1_4_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_09_position_v4.eps}
				\caption{pattern 9}
				\label{figure:simul1_4_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_10_position_v4.eps}
				\caption{pattern 10}
				\label{figure:simul1_4_j}
			\end{subfigure}
			\caption{Patterns of distribution of users in SIMUL1-4.}
			\label{figure:simul1_4_p}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul1_4_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul1_4_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul1_4_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul1_4_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul1_4_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul1_4_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul1_4_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul1_4_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul1_4_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp23_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul1_4_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL1-4.}
			\label{figure:simul1_4_ba}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp23_1-4_utility.eps}
				\caption{sum of utility function}
				\label{figure:simul1_4_u_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.8\textwidth}
				\centering
				\includegraphics[width=10cm]{fig/exp23_1-4_bandwidth.eps}
				\caption{number of users}
				\label{figure:simul1_4_u_b}
			\end{subfigure}
			\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL1-4.}
			\label{figure:simul1_4_u}
		\end{center}
	\end{figure}

%=====================================
%\subsubsection{SIMUL2-1-1}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul2_1_1_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul2_1_1_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul2_1_1_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul2_1_1_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul2_1_1_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul2_1_1_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul2_1_1_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul2_1_1_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul2_1_1_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul2_1_1_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL2-1-1.}
		\label{figure:simul2_1_1_p}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_01_allocated_bandwidth.eps}
			\caption{bandwidth allocation 1}
			\label{figure:simul2_1_1_b_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_02_allocated_bandwidth.eps}
			\caption{bandwidth allocation 2}
			\label{figure:simul2_1_1_b_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_03_allocated_bandwidth.eps}
			\caption{bandwidth allocation 3}
			\label{figure:simul2_1_1_b_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_04_allocated_bandwidth.eps}
			\caption{bandwidth allocation 4}
			\label{figure:simul2_1_1_b_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_05_allocated_bandwidth.eps}
			\caption{bandwidth allocation 5}
			\label{figure:simul2_1_1_b_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_06_allocated_bandwidth.eps}
			\caption{bandwidth allocation 6}
			\label{figure:simul2_1_1_b_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_07_allocated_bandwidth.eps}
			\caption{bandwidth allocation 7}
			\label{figure:simul2_1_1_b_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_08_allocated_bandwidth.eps}
			\caption{bandwidth allocation 8}
			\label{figure:simul2_1_1_b_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_09_allocated_bandwidth.eps}
			\caption{bandwidth allocation 9}
			\label{figure:simul2_1_1_b_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp10_10_allocated_bandwidth.eps}
			\caption{bandwidth allocation 10}
			\label{figure:simul2_1_1_b_j}
		\end{subfigure}
		\caption{Bandwidth allocation in SIMUL2-1-1.}
		\label{figure:simul2_1_1_ba}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp10_2-1-1_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul2_1_1_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp10_2-1-1_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul2_1_1_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL2-1-1.}
		\label{figure:simul2_1_1_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL2-1-2}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp13_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul2_1_2_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp13_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul2_1_2_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp13_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul2_1_2_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp13_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul2_1_2_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp13_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul2_1_2_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp13_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul2_1_2_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp13_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul2_1_2_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp13_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul2_1_2_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp13_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul2_1_2_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp13_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul2_1_2_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL2-1-2.}
		\label{figure:simul2_1_2_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp13_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul2_1_2_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp13_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul2_1_2_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp13_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul2_1_2_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp13_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul2_1_2_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp13_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul2_1_2_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp13_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul2_1_2_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp13_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul2_1_2_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp13_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul2_1_2_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp13_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul2_1_2_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp13_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul2_1_2_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL2-1-2.}
			\label{figure:simul2_1_2_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp13_2-1-2_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul2_1_2_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp13_2-1-2_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul2_1_2_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL2-1-2.}
		\label{figure:simul2_1_2_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL2-2-1}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp11_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul2_2_1_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp11_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul2_2_1_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp11_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul2_2_1_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp11_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul2_2_1_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp11_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul2_2_1_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp11_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul2_2_1_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp11_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul2_2_1_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp11_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul2_2_1_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp11_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul2_2_1_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp11_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul2_2_1_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL2-2-1.}
		\label{figure:simul2_2_1_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp11_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul2_2_1_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp11_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul2_2_1_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp11_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul2_2_1_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp11_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul2_2_1_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp11_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul2_2_1_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp11_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul2_2_1_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp11_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul2_2_1_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp11_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul2_2_1_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp11_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul2_2_1_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp11_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul2_2_1_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL2-2-1.}
			\label{figure:simul2_2_1_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp11_2-2-1_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul2_2_1_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp11_2-2-1_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul2_2_1_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL2-2-1.}
		\label{figure:simul2_2_1_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL2-2-2}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp14_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul2_2_2_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp14_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul2_2_2_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp14_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul2_2_2_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp14_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul2_2_2_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp14_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul2_2_2_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp14_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul2_2_2_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp14_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul2_2_2_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp14_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul2_2_2_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp14_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul2_2_2_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp14_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul2_2_2_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL2-2-2.}
		\label{figure:simul2_2_2_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp14_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul2_2_2_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp14_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul2_2_2_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp14_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul2_2_2_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp14_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul2_2_2_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp14_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul2_2_2_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp14_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul2_2_2_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp14_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul2_2_2_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp14_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul2_2_2_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp14_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul2_2_2_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp14_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul2_2_2_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL2-2-2.}
			\label{figure:simul2_2_2_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp14_2-2-2_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul2_2_2_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp14_2-2-2_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul2_2_2_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL2-2-2.}
		\label{figure:simul2_2_2_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL2-3-1}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp12_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul2_3_1_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp12_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul2_3_1_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp12_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul2_3_1_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp12_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul2_3_1_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp12_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul2_3_1_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp12_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul2_3_1_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp12_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul2_3_1_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp12_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul2_3_1_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp12_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul2_3_1_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp12_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul2_3_1_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL2-3-1.}
		\label{figure:simul2_3_1_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp12_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul2_3_1_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp12_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul2_3_1_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp12_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul2_3_1_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp12_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul2_3_1_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp12_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul2_3_1_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp12_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul2_3_1_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp12_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul2_3_1_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp12_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul2_3_1_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp12_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul2_3_1_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp12_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul2_3_1_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL2-3-1.}
			\label{figure:simul2_3_1_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp12_2-3-1_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul2_3_1_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp12_2-3-1_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul2_3_1_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL2-3-1.}
		\label{figure:simul2_3_1_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL2-3-2}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp15_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul2_3_2_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp15_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul2_3_2_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp15_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul2_3_2_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp15_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul2_3_2_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp15_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul2_3_2_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp15_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul2_3_2_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp15_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul2_3_2_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp15_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul2_3_2_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp15_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul2_3_2_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp15_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul2_3_2_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL2-3-2.}
		\label{figure:simul2_3_2_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp15_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul2_3_2_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp15_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul2_3_2_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp15_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul2_3_2_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp15_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul2_3_2_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp15_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul2_3_2_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp15_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul2_3_2_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp15_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul2_3_2_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp15_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul2_3_2_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp15_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul2_3_2_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp15_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul2_3_2_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL2-3-2.}
			\label{figure:simul2_3_2_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp15_2-3-2_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul2_3_2_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp15_2-3-2_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul2_3_2_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL2-3-2.}
		\label{figure:simul2_3_2_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL2-4}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp16_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul2_4_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp16_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul2_4_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp16_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul2_4_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp16_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul2_4_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp16_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul2_4_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp16_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul2_4_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp16_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul2_4_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp16_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul2_4_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp16_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul2_4_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp16_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul2_4_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL2-4.}
		\label{figure:simul2_4_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp16_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul2_4_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp16_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul2_4_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp16_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul2_4_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp16_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul2_4_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp16_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul2_4_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp16_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul2_4_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp16_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul2_4_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp16_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul2_4_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp16_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul2_4_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp16_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul2_4_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL2-4.}
			\label{figure:simul2_4_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp16_2-4_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul2_4_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp16_2-4_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul2_4_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL2-4.}
		\label{figure:simul2_4_u}
	\end{center}
\end{figure}

\clearpage

%=====================================
%\subsubsection{SIMUL3-1-1}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp24_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul3_1_1_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp24_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul3_1_1_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp24_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul3_1_1_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp24_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul3_1_1_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp24_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul3_1_1_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp24_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul3_1_1_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp24_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul3_1_1_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp24_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul3_1_1_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp24_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul3_1_1_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp24_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul3_1_1_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL3-1-1.}
		\label{figure:simul3_1_1_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp24_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul3_1_1_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp24_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul3_1_1_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp24_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul3_1_1_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp24_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul3_1_1_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp24_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul3_1_1_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp24_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul3_1_1_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp24_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul3_1_1_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp24_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul3_1_1_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp24_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul3_1_1_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp24_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul3_1_1_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL3-1-1.}
			\label{figure:simul3_1_1_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp24_3-1-1_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul3_1_1_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp24_3-1-1_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul3_1_1_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL3-1-1.}
		\label{figure:simul3_1_1_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL3-1-2}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp27_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul3_1_2_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp27_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul3_1_2_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp27_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul3_1_2_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp27_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul3_1_2_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp27_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul3_1_2_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp27_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul3_1_2_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp27_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul3_1_2_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp27_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul3_1_2_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp27_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul3_1_2_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp27_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul3_1_2_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL3-1-2.}
		\label{figure:simul3_1_2_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp27_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul3_1_2_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp27_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul3_1_2_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp27_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul3_1_2_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp27_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul3_1_2_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp27_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul3_1_2_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp27_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul3_1_2_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp27_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul3_1_2_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp27_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul3_1_2_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp27_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul3_1_2_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp27_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul3_1_2_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL3-1-2.}
			\label{figure:simul3_1_2_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp27_3-1-2_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul3_1_2_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp27_3-1-2_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul3_1_2_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL3-1-2.}
		\label{figure:simul3_1_2_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL3-2-1}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp25_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul3_2_1_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp25_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul3_2_1_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp25_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul3_2_1_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp25_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul3_2_1_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp25_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul3_2_1_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp25_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul3_2_1_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp25_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul3_2_1_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp25_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul3_2_1_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp25_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul3_2_1_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp25_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul3_2_1_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL3-2-1.}
		\label{figure:simul3_2_1_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp25_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul3_2_1_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp25_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul3_2_1_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp25_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul3_2_1_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp25_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul3_2_1_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp25_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul3_2_1_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp25_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul3_2_1_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp25_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul3_2_1_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp25_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul3_2_1_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp25_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul3_2_1_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp25_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul3_2_1_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL3-2-1.}
			\label{figure:simul3_2_1_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp25_3-2-1_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul3_2_1_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp25_3-2-1_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul3_2_1_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL3-2-1.}
		\label{figure:simul3_2_1_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL3-2-2}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp28_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul3_2_2_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp28_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul3_2_2_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp28_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul3_2_2_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp28_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul3_2_2_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp28_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul3_2_2_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp28_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul3_2_2_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp28_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul3_2_2_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp28_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul3_2_2_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp28_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul3_2_2_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp28_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul3_2_2_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL3-2-2.}
		\label{figure:simul3_2_2_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp28_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul3_2_2_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp28_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul3_2_2_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp28_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul3_2_2_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp28_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul3_2_2_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp28_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul3_2_2_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp28_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul3_2_2_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp28_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul3_2_2_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp28_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul3_2_2_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp28_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul3_2_2_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp28_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul3_2_2_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL3-2-2.}
			\label{figure:simul3_2_2_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp28_3-2-2_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul3_2_2_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp28_3-2-2_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul3_2_2_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL3-2-2.}
		\label{figure:simul3_2_2_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL3-3-1}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp26_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul3_3_1_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp26_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul3_3_1_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp26_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul3_3_1_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp26_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul3_3_1_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp26_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul3_3_1_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp26_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul3_3_1_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp26_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul3_3_1_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp26_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul3_3_1_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp26_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul3_3_1_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp26_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul3_3_1_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL3-3-1.}
		\label{figure:simul3_3_1_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp26_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul3_3_1_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp26_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul3_3_1_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp26_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul3_3_1_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp26_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul3_3_1_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp26_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul3_3_1_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp26_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul3_3_1_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp26_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul3_3_1_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp26_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul3_3_1_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp26_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul3_3_1_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp26_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul3_3_1_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL3-3-1.}
			\label{figure:simul3_3_1_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp26_3-3-1_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul3_3_1_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp26_3-3-1_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul3_3_1_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL3-3-1.}
		\label{figure:simul3_3_1_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL3-3-2}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp29_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul3_3_2_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp29_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul3_3_2_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp29_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul3_3_2_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp29_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul3_3_2_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp29_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul3_3_2_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp29_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul3_3_2_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp29_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul3_3_2_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp29_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul3_3_2_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp29_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul3_3_2_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp29_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul3_3_2_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL3-3-2.}
		\label{figure:simul3_3_2_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp29_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul3_3_2_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp29_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul3_3_2_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp29_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul3_3_2_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp29_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul3_3_2_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp29_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul3_3_2_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp29_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul3_3_2_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp29_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul3_3_2_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp29_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul3_3_2_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp29_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul3_3_2_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp29_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul3_3_2_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL3-3-2.}
			\label{figure:simul3_3_2_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp29_3-3-2_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul3_3_2_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp29_3-3-2_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul3_3_2_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL3-3-2.}
		\label{figure:simul3_3_2_u}
	\end{center}
\end{figure}

\clearpage

%\subsubsection{SIMUL3-4}
\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp30_01_position_v4.eps}
			\caption{pattern 1}
			\label{figure:simul3_4_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp30_02_position_v4.eps}
			\caption{pattern 2}
			\label{figure:simul3_4_b}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp30_03_position_v4.eps}
			\caption{pattern 3}
			\label{figure:simul3_4_c}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp30_04_position_v4.eps}
			\caption{pattern 4}
			\label{figure:simul3_4_d}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp30_05_position_v4.eps}
			\caption{pattern 5}
			\label{figure:simul3_4_e}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp30_06_position_v4.eps}
			\caption{pattern 6}
			\label{figure:simul3_4_f}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp30_07_position_v4.eps}
			\caption{pattern 7}
			\label{figure:simul3_4_g}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp30_08_position_v4.eps}
			\caption{pattern 8}
			\label{figure:simul3_4_h}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp30_09_position_v4.eps}
			\caption{pattern 9}
			\label{figure:simul3_4_i}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[width=\textwidth]{fig/exp30_10_position_v4.eps}
			\caption{pattern 10}
			\label{figure:simul3_4_j}
		\end{subfigure}
		\caption{Patterns of distribution of users in SIMUL3-4.}
		\label{figure:simul3_4_p}
	\end{center}
\end{figure}

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp30_01_allocated_bandwidth.eps}
				\caption{bandwidth allocation 1}
				\label{figure:simul3_4_b_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp30_02_allocated_bandwidth.eps}
				\caption{bandwidth allocation 2}
				\label{figure:simul3_4_b_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp30_03_allocated_bandwidth.eps}
				\caption{bandwidth allocation 3}
				\label{figure:simul3_4_b_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp30_04_allocated_bandwidth.eps}
				\caption{bandwidth allocation 4}
				\label{figure:simul3_4_b_d}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp30_05_allocated_bandwidth.eps}
				\caption{bandwidth allocation 5}
				\label{figure:simul3_4_b_e}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp30_06_allocated_bandwidth.eps}
				\caption{bandwidth allocation 6}
				\label{figure:simul3_4_b_f}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp30_07_allocated_bandwidth.eps}
				\caption{bandwidth allocation 7}
				\label{figure:simul3_4_b_g}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp30_08_allocated_bandwidth.eps}
				\caption{bandwidth allocation 8}
				\label{figure:simul3_4_b_h}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp30_09_allocated_bandwidth.eps}
				\caption{bandwidth allocation 9}
				\label{figure:simul3_4_b_i}
			\end{subfigure}
			\begin{subfigure}[b]{0.32\textwidth}
				\includegraphics[width=\textwidth]{fig/exp30_10_allocated_bandwidth.eps}
				\caption{bandwidth allocation 10}
				\label{figure:simul3_4_b_j}
			\end{subfigure}
			\caption{Bandwidth allocation in SIMUL3-4.}
			\label{figure:simul3_4_ba}
		\end{center}
	\end{figure}

\begin{figure}
	\begin{center}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp30_3-4_utility.eps}
			\caption{sum of utility function}
			\label{figure:simul3_4_u_a}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[width=10cm]{fig/exp30_3-4_bandwidth.eps}
			\caption{number of users}
			\label{figure:simul3_4_u_b}
		\end{subfigure}
		\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL3-4.}
		\label{figure:simul3_4_u}
	\end{center}
\end{figure}

\clearpage

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Evaluation_for_AP_Association.tex
update

% Evaluation for AP Association
\section{Evaluation for AP Association}
	We will evaluate our algorithm CVXP by simulation and compare the result of CVXP to the result of a naive algorithm HDR that each user associates with the AP which provides the greatest bit rate to the user. We evaluate the sum of the utility function when the distribution of users' position is uniform, dense in a region, or random as well as the number of antennas of each user is uniform or random.

	We design $3$ experiments. In each experiment, we place $16$ APs on a $4\times4$ grid whose spacing is $100 M$ in a $500M \times 500M$ square. Fig. \ref{figure:exp08_p_a_v1} shows the distribution of APs. The transmit power of each antenna on an AP can be set $17 dBm$, $14 dBm$, or $11 dBm$. The radius of the coverage of the antenna corresponding to the power $17 dBm$, $14 dBm$, and $11 dBm$ is $150 M$, $100 M$, and $70 M$. There are $3$ antennas on each AP and the power of each antenna on each AP will be set $17 dBm$, $14 dBm$, and $11 dBm$ respectively.

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp08_position_ap_v1.png}
				\caption{The distribution of APs on a $4 \times 4$ grid in a $500M \times 500M$ square.}
				\label{figure:exp08_p_a_v1}
			\end{center}
		\end{figure}

\subsection{Experiment 1}
	There are $441$ users distributed uniformly in the square. The position and the number of antennas on each user are shown in Fig. \ref{figure:exp05_p_v4}. The color of a point means the number of antennas on the user. In this experiment, each user has $2$ antennas. We perform our AP association algorithm CVXP as well as high data rate algorithm HDR respectively and then observe the bandwidth allocation and the sum of the utility function.

	Fig. \ref{figure:exp05_a_b} shows the bandwidth allocation and the sum of the utility function of CVXP and HDR respectively. The value of the point on the red line (green line) means the amount of the bandwidth allocated to the corresponding user by CVXP (HDR). There are $47\%$ users obtaining more bandwidth from CVXP than HDR. There are $31\%$ users obtaining more bandwidth from HDR than CVXP. The sum of the utility function of CVXP is $144.988$ which is greater than the sum of the utility function of HDR which is $136.479$. We can say that CVXP outperforms HDR.

	Fig. \ref{figure:exp05_s_b_b_t_a_b_r_t_v2} shows the relation between the allocated bandwidth and the receiving time for each user. Although the maximum of the allocated bandwidth is 52 times as much as the minimum of the allocated bandwidth, the maximum of the receiving time is 5.2 times as much as the minimum of the receiving time. All users have non-zero time to receive data. We also can observe that although each user has 2 antennas, the receiving time is no more than 1 second. The reason may be the number of antennas on the AP is not enough to allocate more receiving time to users.

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp05_position_v4.png}
				\caption{The distribution of APs on a $4 \times 4$ grid and users in a $500M \times 500M$ square.}
				\label{figure:exp05_p_v4}
			\end{center}
		\end{figure}

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp05_allocated_bandwidth.png}
				\caption{The sorted allocated bandwidth in non-decreasing order.}
				\label{figure:exp05_a_b}
			\end{center}
		\end{figure}

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp05_sorted_by_bw_time_allocated_bandwidth_receiving_time_v2.png}
				\caption{The sorted allocated bandwidth and the corresponding receiving time.}
				\label{figure:exp05_s_b_b_t_a_b_r_t_v2}
			\end{center}
		\end{figure}

\subsection{Experiment 2}
	There are $441$ users with different number of antennas distributed uniformly in the square. The position and the number of antennas on each user are shown in Fig. \ref{figure:exp07_p_v4}. The color represents the number of antennas.

	Fig. \ref{figure:exp07_a_b} shows the amount of the bandwidth allocated to each user and the sum of the utility function by CVXP and HDR. In this experiment, there are $28\%$ users allocated more bandwidth by HDR than CVXP. There are $48\%$ users allocated more bandwidth by CVXP than HDR. The sum of the utility function of CVXP is $146.695$ and that of HDR is $136.479$. We can say that CVXP outperforms HDR.

	Fig. \ref{figure:exp07_s_b_b_t_a_b_r_t_v2} shows the allocated bandwidth and the corresponding receiving time of each user by CVXP. The maximum of allocated bandwidth is $48$ times as much as the minimum of that. The maximum of receiving time is $4.8$ times as much as the minimum of that. The proportional criterion makes the deviation of the receiving time smaller when we compare it with the deviation of the allocated bandwidth.

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp07_position_v4.png}
				\caption{The distribution of APs on a $4 \times 4$ grid and users in a $500M \times 500M$ square.}
				\label{figure:exp07_p_v4}
			\end{center}
		\end{figure}

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp07_allocated_bandwidth.png}
				\caption{The sorted allocated bandwidth in non-decreasing order.}
				\label{figure:exp07_a_b}
			\end{center}
		\end{figure}

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp07_sorted_by_bw_time_allocated_bandwidth_receiving_time_v2.png}
				\caption{The sorted allocated bandwidth and the corresponding receiving time.}
				\label{figure:exp07_s_b_b_t_a_b_r_t_v2}
			\end{center}
		\end{figure}

\subsection{Experiment 3}
	There are $441$ users with different numbers of the antennas in the square. There are $289$ users among them distributed densely in the lower left region of the square. Each user has the same number of antennas as in experiment 2. The position and the number of antennas on each user are shown in Fig. \ref{figure:exp08_p_v4}.

	Fig. \ref{figure:exp08_a_b} shows the amount of the bandwidth allocated to each user and the sum of the utility function by CVXP and HDR. There are $85\%$ users to be allocated more bandwidth by CVXP than HDR. There are $15\%$ users to be allocated more bandwidth by HDR than CVXP. The sum of the utility function of CVXP is $101.205$. The sum of the utility function of HDR is $57.8207$. We can say that CVXP outperforms HDR in this experiment.

	Fig. \ref{figure:exp08_s_b_b_t_a_b_r_t_v2} shows the allocated bandwidth and the corresponding receiving time of each user by CVXP. The maximum of allocated bandwidth is $485$ times as much as the minimum of that. The maximum of receiving time is $48.5$ times as much as the minimum of that.

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp08_position_v4.png}
				\caption{The distribution of APs on a $4 \times 4$ grid and users in a $500M \times 500M$ square.}
				\label{figure:exp08_p_v4}
			\end{center}
		\end{figure}

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp08_allocated_bandwidth.png}
				\caption{The sorted allocated bandwidth in non-decreasing order.}
				\label{figure:exp08_a_b}
			\end{center}
		\end{figure}

		\begin{figure}
			\begin{center}
				\includegraphics[width=10cm]{fig/exp08_sorted_by_bw_time_allocated_bandwidth_receiving_time_v2.png}
				\caption{The sorted allocated bandwidth and the corresponding receiving time.}
				\label{figure:exp08_s_b_b_t_a_b_r_t_v2}
			\end{center}
		\end{figure}

\subsection{Experiment 4}
There are $441$ users with different numbers of the antennas distributed randomly in the square. Each user has the same number of antennas as in experiment 2. The position and the number of antennas on each user are shown in Fig. \ref{figure:exp09_p_v4}.

Fig. \ref{figure:exp09_a_b} shows the amount of the bandwidth allocated to each user and the sum of the utility function by CVXP and HDR. There are $51\%$ users to be allocated more bandwidth by CVXP than HDR. There are $45\%$ users to be allocated more bandwidth by HDR than CVXP. The sum of the utility function of CVXP is $206.785$. The sum of the utility function of HDR is $202.539$. We can say that CVXP outperforms HDR in this experiment.

Fig. \ref{figure:exp09_s_b_b_t_a_b_r_t_v2} shows the allocated bandwidth and the corresponding receiving time of each user by CVXP. The maximum of allocated bandwidth is $86$ times as much as the minimum of that. The maximum of receiving time is $8.6$ times as much as the minimum of that.

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{fig/exp09_position_v4.png}
		\caption{The distribution of APs on a $4 \times 4$ grid and users in a $500M \times 500M$ square.}
		\label{figure:exp09_p_v4}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{fig/exp09_allocated_bandwidth.png}
		\caption{The sorted allocated bandwidth in non-decreasing order.}
		\label{figure:exp09_a_b}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{fig/exp09_sorted_by_bw_time_allocated_bandwidth_receiving_time_v2.png}
		\caption{The sorted allocated bandwidth and the corresponding receiving time.}
		\label{figure:exp09_s_b_b_t_a_b_r_t_v2}
	\end{center}
\end{figure}

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Evaluation_for_AP_Association_2.tex
update

% Evaluation of AP Association 2 (2015-7-2)
\section{Evaluation for AP Association}
	We will evaluate the results of the following algorithms:
	\begin{itemize}
		\item Our algorithm CVXP, which associates users to APs according to the solution of the corresponding convex program.
		\item A naive algorithm HDR, which associates a user to an AP which provides the greatest sum of bit rate to the user.
	\end{itemize}
	After performing above algorithms, we will run the bandwidth allocation algorithm for each set of users who associate with the same AP. Each user will obtain bandwidth allocated by the algorithm.

	We will compare two values count from the results of CVXP and HDR as follows:
	\begin{itemize}
		\item The sum of the utility function of the bandwidth of each user. We can refer to this value as the total satisfaction of all users. We would like to maximize the total satisfaction. When the total satisfaction is maximum, the allocated bandwidth is under proportional fairness criterion.
		\item The number of users who obtain more bandwidth from CVXP and HDR. This value can show which algorithm can bring benefit to more users.
	\end{itemize}

	In the simulation setting for APs, we assume all APs use different channels so that they will not interfere to each other. In reality, we can deploy APs in a region by prior arrangement to avoid interference. We let each AP have $3$ antennas. The transmit power of antennas is set to $17 dBm$, $14 dBm$, and $11 dBm$, respectively. The radius of the coverage of the antenna with power $17 dBm$, $14 dBm$, and $11 dBm$ is $150 M$, $100 M$, and $70 M$, respectively. In our simulations, the user bit rate depends on the transmit power of the antenna on the AP and the distance between the user and the AP. The user bit rate information is shown in Table \ref{Tab:drol}.

	In the simulation setting for users, we set the range of the number of antennas on each user is from $1$ to $3$ and assign the number to the user randomly. We assume the user bit rate from any antenna on the user to the same antenna on the AP is the same. The position of each user in the simulation is fixed.

	In each simulation, we place $16$ APs on a $4 \times 4$ grid whose spacing is $100 M$. The grid is put in the center of a $500 M \times 500 M$ square. Fig. \ref{figure:exp08_p_a_v1} shows the deployment of APs. All users are put in the square so that we can make sure that each user has at least one AP to associate with.

	\begin{figure}
		\begin{center}
			\includegraphics[width=10cm]{fig/exp08_position_ap_v1.eps}
			\caption{The deployment of APs on a $4 \times 4$ grid in the center of a $500 M \times 500 M$ square.}
			\label{figure:exp08_p_a_v1}
		\end{center}
	\end{figure}

	We evaluate CVXP and HDR for the various number of users and the various distribution of positions of users in the square. We will perform $3$ sets of simulations different in the number of users in the square. The number of users in simulations are $225$, $441$, and $666$, respectively. The simulations are perfromed from moderately loaded network to heavily loaded network.

	In each set of simulations, the distributions of positions of users are various. We consider two kinds of distributions. First, the distribution is uniform. Second, the distribution has a hot spot which means a location where most users reside in. In order to simulate the distribution with a hot spot, we separate the square into $3 \times 3$ sub-squares and choose one sub-square as a hot spot, shown as Fig. \ref{figure:hotspot}. Because the square is symmetric, we will only simulate the center sub-square, the middle-left sub-square, and the lower-left sub-square as the hot spot, respectively.

	\begin{figure}
		\begin{center}
			\includegraphics[width=5cm]{fig/hotspot.png}
			\caption{The square is separated to $3 \times 3$ sub-squares. The number in each sub-square means the number of users in the sub-square. In this figure, the hot spot is the center sub-square.}
			\label{figure:hotspot}
		\end{center}
	\end{figure}

	For describing conveniently, we will call the set of simulations with $225$, $441$, $666$ users SIMUL1, SIMUL2, SIMUL3.

	In SIMUL1, we will perform $4$ simulations, termed SIMUL1-1, SIMUL1-2, SIMUL1-3, and SIMUL1-4. In SIMUL1-1, SIMUL1-2, and SIMUL1-3, we simulate the distribution with a hot spot in the center, middle-left, and lower-left sub-square, respectively. In SIMUL1-4, we simulate the distribution is uniform.

	In SIMUL1-1, we will perform $2$ simulations, termed SIMUL1-1-1 and SIMUL1-1-2. We model a moderately hot spot and a heavily hot spot in these simulations. The difference is the number of users in the hot spot.

	SIMUL1-2 and SIMUL1-3 are planned by the same rule as SIMUL1-1. SIMUL2 and SIMUL3 are planned by the same as SIMUL1.

	We solve the convex program using CVX which is a Matlab-based modeling system for convex optimization (http://cvxr.com/cvx/).

	Next, we will show the setting and the result of each simulation. In each simulation, we will generate $10$ patterns of the distribution of positions of users such that the number of users in each sub-square is the same as the setting.

%=========
%=========
\subsection{SIMUL1}
	In SIMUL1, the number of users in the square is $225$. The number of users in each sub-square is shown in Table \ref{Tab:nouies1}. We will simulate as follows: 
	\begin{itemize}
		\item The hot spot is in the center, middle-left, and lower-left sub-square.
		\item The number of users in each sub-square is the same.
	\end{itemize}

	\begin{table} \small
		\centering \caption{Number of users in each sub-square in SIMUL1}
		\renewcommand\arraystretch{1.0}
		\begin{tabular}{|r||c||c||c||c||c||c||c|} % m{5.38cm}
			\hline
			&\multicolumn{7}{|c|}{Simulation} \\
			\hline	sub-square & 1-1-1 & 1-1-2 & 1-2-1 & 1-2-2 & 1-3-1 & 1-3-2 & 1-4 \\
			\hline
			\hline	lower-left & $11$ & $19$ & $20$ & $25$ & $123$ & $75$ & $25$ \\
			\hline	middle-left & $15$ & $19$ & $123$ & $75$ & $20$ & $25$ & $25$ \\
			\hline	upper-left & $10$ & $19$ & $20$ & $25$ & $8$ & $15$ & $25$ \\
			\hline	lower-middle & $15$ & $19$ & $9$ & $15$ & $20$ & $25$ & $25$ \\
			\hline	center & $123$ & $75$ & $20$ & $25$ & $20$ & $25$ & $25$ \\
			\hline	upper-middle & $15$ & $18$ & $9$ & $15$ & $9$ & $15$ & $25$ \\
			\hline	lower-right & $10$ & $18$ & $8$ & $15$ & $8$ & $15$ & $25$ \\
			\hline	middle-right & $15$ & $19$ & $8$ & $15$ & $9$ & $15$ & $25$ \\
			\hline	upper-right & $11$ & $19$ & $8$ & $15$ & $8$ & $15$ & $25$ \\
			\hline
		\end{tabular}\label{Tab:nouies1}
	\end{table}

	Fig. \ref{figure:simul1} and Table \ref{Tab:simul1} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth in each simulation. We can see that in both comparisons CVXP performs better than HDR.

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.4\textwidth}
				\includegraphics[width=6cm]{fig/simul1_utility.eps}
				\caption{sum of utility function}
				\label{figure:simul1_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.4\textwidth}
				\includegraphics[width=6cm]{fig/simul1_users.eps}
				\caption{number of users}
				\label{figure:simul1_b}
			\end{subfigure}
			\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL1.}
			\label{figure:simul1}
		\end{center}
	\end{figure}

	\begin{table} \small
		\centering \caption{Sum of utility function and number of users obtaining more bandwidth in SIMUL1.}
		\renewcommand\arraystretch{1.0}
		\begin{tabular}{|c||c|c||c|c||c|c||c|c|} % m{5.38cm}
			\hline
			&\multicolumn{4}{|c||}{Sum of utility function} & \multicolumn {4}{|c|}{Number of users} \\
			\hline & \multicolumn{2}{|c||}{CVXP} & \multicolumn{2}{|c||}{HDR} & \multicolumn{2}{|c||}{CVXP} & \multicolumn{2}{|c|}{HDR} \\
			\hline	Simulation & AVG & STD & AVG & STD & AVG & STD & AVG & STD \\
			\hline
			\hline	1-1-1 & $182$ & $5$ & $179$ & $5$ & $64\%$ & $5\%$ & $30\%$ & $6\%$ \\
			\hline	1-1-2 & $178$ & $6$ & $176$ & $7$ & $49\%$ & $10\%$ & $35\%$ & $6\%$ \\
			\hline	1-2-1 & $134$ & $8$ & $123$ & $7$ & $63\%$ & $3\%$ & $34\%$ & $4\%$ \\
			\hline	1-2-2 & $155$ & $5$ & $150$ & $5$ & $60\%$ & $4\%$ & $34\%$ & $3\%$ \\
			\hline	1-3-1 & $99$ & $6$ & $80$ & $7$ & $56\%$ & $4\%$ & $41\%$ & $4\%$ \\
			\hline	1-3-2 & $142$ & $7$ & $134$ & $7$ & $54\%$ & $5\%$ & $40\%$ & $5\%$ \\
			\hline	1-4 & $161$ & $3$ & $158$ & $3$ & $53\%$ & $7\%$ & $34\%$ & $4\%$ \\
			\hline
		\end{tabular}\label{Tab:simul1}
	\end{table}	
	When we observe Fig. \ref{figure:simul1_a}, we can see some trends. First, when the hot spot is the center sub-square (the lower-left sub-square), the sum of the utility function (i.e., the total satisfaction) is the greatest (smallest). It makes sense because users in the center sub-square have more choices of APs for AP association than users in the lower-left sub-square. CVXP also performs better when the hot spot is the center sub-square than the number of users in each sub-square is uniform. This is because our deployment of APs is uniform in the square, users near the margin of the square have less choice of APs for AP association.

	Second, the sum of the utility function in the moderately loaded hot spot in the middle-left or lower-left sub-square is better than that in the heavily loaded hot spot in the middle-left or lower-left sub-square. It makes sense because APs in the moderately loaded hot spot may be associated with less users and obtain better the sum of the utility function.

	Fig. \ref{figure:simul1_b} shows CVXP makes more users obtaining more bandwidth than HDR in all hot spot and uniform simulations.

	The details of each simulation are shown in Appendix \ref{apendix:dos}.
%=========
%\subsubsection{SIMUL1-1-1}
%\subsubsection{SIMUL1-1-2}
%\subsubsection{SIMUL1-2-1}
%\subsubsection{SIMUL1-2-2}
%\subsubsection{SIMUL1-3-1}
%\subsubsection{SIMUL1-3-2}
%\subsubsection{SIMUL1-4}

%=========
%=========
\subsection{SIMUL2}
	In SIMUL2, the number of users in the square is $441$. The number of users in each sub-square is shown in Table \ref{Tab:nouies2}. We will simulate as follows: 
	\begin{itemize}
		\item The hot spot is in the center, middle-left, and lower-left sub-square.
		\item The number of users in each sub-square is the same.
	\end{itemize}

	\begin{table} \small
		\centering \caption{Number of users in each sub-square in SIMUL2}
		\renewcommand\arraystretch{1.0}
		\begin{tabular}{|r||c||c||c||c||c||c||c|} % m{5.38cm}
			\hline
			&\multicolumn{7}{|c|}{Simulation} \\
			\hline	sub-square & 2-1-1 & 2-1-2 & 2-2-1 & 2-2-2 & 2-3-1 & 2-3-2 & 2-4 \\
			\hline
			\hline	lower-left & $19$ & $37$ & $40$ & $49$ & $246$ & $147$ & $49$ \\
			\hline	middle-left & $30$ & $37$ & $246$ & $147$ & $40$ & $49$ & $49$ \\
			\hline	upper-left & $19$ & $37$ & $40$ & $49$ & $15$ & $29$ & $49$ \\
			\hline	lower-middle & $30$ & $36$ & $15$ & $29$ & $40$ & $49$ & $49$ \\
			\hline	center & $245$ & $147$ & $40$ & $49$ & $40$ & $49$ & $49$ \\
			\hline	upper-middle & $30$ & $36$ & $15$ & $29$ & $15$ & $30$ & $49$ \\
			\hline	lower-right & $19$ & $37$ & $15$ & $30$ & $15$ & $29$ & $49$ \\
			\hline	middle-right & $30$ & $37$ & $15$ & $29$ & $15$ & $30$ & $49$ \\
			\hline	upper-right & $19$ & $37$ & $15$ & $30$ & $15$ & $29$ & $49$ \\
			\hline
		\end{tabular}\label{Tab:nouies2}
	\end{table}

	Fig. \ref{figure:simul2} and Table \ref{Tab:simul2} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth in each simulation. We can see that in both comparisons CVXP performs better than HDR.

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.4\textwidth}
				\includegraphics[width=6cm]{fig/simul2_utility.eps}
				\caption{sum of utility function}
				\label{figure:simul2_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.4\textwidth}
				\includegraphics[width=6cm]{fig/simul2_users.eps}
				\caption{number of users}
				\label{figure:simul2_b}
			\end{subfigure}
			\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL2.}
			\label{figure:simul2}
		\end{center}
	\end{figure}

	\begin{table} \small
		\centering \caption{Sum of utility function and number of users obtaining more bandwidth in SIMUL2.}
		\renewcommand\arraystretch{1.0}
		\begin{tabular}{|c||c|c||c|c||c|c||c|c|} % m{5.38cm}
			\hline
			&\multicolumn{4}{|c||}{Sum of utility function} & \multicolumn {4}{|c|}{Number of users} \\
			\hline & \multicolumn{2}{|c||}{CVXP} & \multicolumn{2}{|c||}{HDR} & \multicolumn{2}{|c||}{CVXP} & \multicolumn{2}{|c|}{HDR} \\
			\hline	Simulation & AVG & STD & AVG & STD & AVG & STD & AVG & STD \\
			\hline
			\hline	2-1-1 & $229$ & $5$ & $224$ & $5$ & $61\%$ & $7\%$ & $32\%$ & $7\%$ \\
			\hline	2-1-2 & $223$ & $4$ & $220$ & $4$ & $54\%$ & $7\%$ & $33\%$ & $6\%$ \\
			\hline	2-2-1 & $125$ & $6$ & $105$ & $7$ & $65\%$ & $3\%$ & $32\%$ & $2\%$ \\
			\hline	2-2-2 & $181$ & $6$ & $170$ & $7$ & $58\%$ & $3\%$ & $40\%$ & $3\%$ \\
			\hline	2-3-1 & $67$ & $6$ & $31$ & $8$ & $55\%$ & $4\%$ & $43\%$ & $3\%$ \\
			\hline	2-3-2 & $149$ & $6$ & $133$ & $7$ & $49\%$ & $5\%$ & $47\%$ & $4\%$ \\
			\hline	2-4 & $192$ & $11$ & $188$ & $11$ & $53\%$ & $5\%$ & $39\%$ & $5\%$ \\
			\hline
		\end{tabular}\label{Tab:simul2}
	\end{table}	
	When we observe Fig. \ref{figure:simul2_a}, we can see the same trends as SIMUL1. First, when the hot spot is the center sub-square (the lower-left sub-square), the sum of the utility function (i.e., the total satisfaction) is the greatest (smallest). The reason is the same as SIMUL1 that users in the center sub-square have more choices of APs for AP association than users in the lower-left sub-square. CVXP also performs better when the hot spot is the center sub-square than the number of users in each sub-square is uniform. This is because our deployment of APs is uniform in the square, users near the margin of the square have less choice of APs for AP association.

	Second, the sum of the utility function in the moderately loaded hot spot in the middle-left or lower-left sub-square is also better than that in the heavily loaded hot spot in the middle-left or lower-left sub-square. It makes sense because APs in the moderately loaded hot spot may be associated with less users and obtain better the sum of the utility function.

	Fig. \ref{figure:simul2_b} shows CVXP makes more users obtaining more bandwidth than HDR in all hot spot and uniform simulations.

	The details of each simulation are shown in Appendix \ref{apendix:dos}.
	%=========
%\subsubsection{SIMUL2-1-1}
%\subsubsection{SIMUL2-1-2}
%\subsubsection{SIMUL2-2-1}
%\subsubsection{SIMUL2-2-2}
%\subsubsection{SIMUL2-3-1}
%\subsubsection{SIMUL2-3-2}
%\subsubsection{SIMUL2-4}

%=========
%=========
\subsection{SIMUL3}
	In SIMUL3, the number of users in the square is $666$. The number of users in each sub-square is shown in Table \ref{Tab:nouies3}. We will simulate as follows: 
	\begin{itemize}
		\item The hot spot is in the center, middle-left, and lower-left sub-square.
		\item The number of users in each sub-square is the same.
	\end{itemize}

	\begin{table} \small
		\centering \caption{Number of users in each sub-square in SIMUL3}
		\renewcommand\arraystretch{1.0}
		\begin{tabular}{|r||c||c||c||c||c||c||c|} % m{5.38cm}
			\hline
			&\multicolumn{7}{|c|}{Simulation} \\
			\hline	sub-square & 3-1-1 & 3-1-2 & 3-2-1 & 3-2-2 & 3-3-1 & 3-3-2 & 3-4 \\
			\hline
			\hline	lower-left & $30$ & $56$ & $60$ & $74$ & $369$ & $222$ & $74$ \\
			\hline	middle-left & $45$ & $56$ & $369$ & $222$ & $60$ & $74$ & $74$ \\
			\hline	upper-left & $29$ & $56$ & $60$ & $74$ & $23$ & $44$ & $74$ \\
			\hline	lower-middle & $45$ & $55$ & $24$ & $44$ & $60$ & $74$ & $74$ \\
			\hline	center & $368$ & $222$ & $60$ & $74$ & $60$ & $74$ & $74$ \\
			\hline	upper-middle & $45$ & $54$ & $24$ & $44$ & $24$ & $45$ & $74$ \\
			\hline	lower-right & $29$ & $55$ & $23$ & $45$ & $23$ & $44$ & $74$ \\
			\hline	middle-right & $45$ & $56$ & $23$ & $44$ & $24$ & $45$ & $74$ \\
			\hline	upper-right & $30$ & $56$ & $23$ & $45$ & $23$ & $44$ & $74$ \\
			\hline
		\end{tabular}\label{Tab:nouies3}
	\end{table}

	Fig. \ref{figure:simul3} and Table \ref{Tab:simul3} shows the comparison of the sum of the utility function and the number of users obtaining more bandwidth in each simulation. We can see that in both comparisons CVXP performs better than HDR.

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.4\textwidth}
				\includegraphics[width=6cm]{fig/simul3_utility.eps}
				\caption{sum of utility function}
				\label{figure:simul3_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.4\textwidth}
				\includegraphics[width=6cm]{fig/simul3_users.eps}
				\caption{number of users}
				\label{figure:simul3_b}
			\end{subfigure}
			\caption{Comparison of sum of utility function and number of users obtaining more bandwidth in SIMUL3.}
			\label{figure:simul3}
		\end{center}
	\end{figure}

	\begin{table} \small
		\centering \caption{Sum of utility function and number of users obtaining more bandwidth in SIMUL3.}
		\renewcommand\arraystretch{1.0}
		\begin{tabular}{|c||c|c||c|c||c|c||c|c|} % m{5.38cm}
			\hline
			&\multicolumn{4}{|c||}{Sum of utility function} & \multicolumn {4}{|c|}{Number of users} \\
			\hline & \multicolumn{2}{|c||}{CVXP} & \multicolumn{2}{|c||}{HDR} & \multicolumn{2}{|c||}{CVXP} & \multicolumn{2}{|c|}{HDR} \\
			\hline	Simulation & AVG & STD & AVG & STD & AVG & STD & AVG & STD \\
			\hline
			\hline	3-1-1 & $228$ & $8$ & $220$ & $9$ & $62\%$ & $5\%$ & $33\%$ & $3\%$ \\
			\hline	3-1-2 & $221$ & $7$ & $216$ & $7$ & $54\%$ & $5\%$ & $37\%$ & $4\%$ \\
			\hline	3-2-1 & $79$ & $14$ & $48$ & $17$ & $64\%$ & $2\%$ & $34\%$ & $3\%$ \\
			\hline	3-2-2 & $147$ & $13$ & $135$ & $14$ & $56\%$ & $3\%$ & $40\%$ & $2\%$ \\
			\hline	3-3-1 & $-13$ & $14$ & $-66$ & $14$ & $53\%$ & $4\%$ & $45\%$ & $4\%$ \\
			\hline	3-3-2 & $112$ & $14$ & $89$ & $14$ & $50\%$ & $4\%$ & $46\%$ & $3\%$ \\
			\hline	4-4 & $172$ & $9$ & $167$ & $9$ & $55\%$ & $3\%$ & $39\%$ & $2\%$ \\
			\hline
		\end{tabular}\label{Tab:simul3}
	\end{table}	
	The same trends as SIMUL1 and SIMUL2 are shown in Fig. \ref{figure:simul3_a}. When the hot spot is the center sub-square (the lower-left sub-square), the sum of the utility function (i.e., the total satisfaction) is the greatest (smallest). The reason is the same as SIMUL1 and SIMUL2 that users in the center sub-square have more choices of APs for AP association than users in the lower-left sub-square. CVXP also performs better when the hot spot is the center sub-square than the distribution of users is uniform. This is because our deployment of APs is uniform in the square, users near the margin of the square have less choice of APs for AP association.

	The sum of the utility function in the moderately loaded hot spot in the middle-left or lower-left sub-square is also better than that in the heavily loaded hot spot in the middle-left or lower-left sub-square. It makes sense because APs in the moderately loaded hot spot may be associated with less users and obtain better the sum of the utility function.

	Fig. \ref{figure:simul3_b} shows CVXP makes more users obtaining more bandwidth than HDR in all hot spot and uniform simulations.

	The details of each simulation are shown in Appendix \ref{apendix:dos}.
	%=========
%\subsubsection{SIMUL3-1-1}
%\subsubsection{SIMUL3-1-2}
%\subsubsection{SIMUL3-2-1}
%\subsubsection{SIMUL3-2-2}
%\subsubsection{SIMUL3-3-1}
%\subsubsection{SIMUL3-3-2}
%\subsubsection{SIMUL3-4}

%=========
\subsection{Comparison of SIMUL1, 2, and 3}
	Fig.\ref{figure:simul123} shows the comparison of SIMUL1, 2, and 3 in each hot spot simulation and uniform number of users simulation. In Fig.\ref{figure:simul123_a}, the hot spot is in the center sub-square. When the number of users increases, the sum of the utility function increases, too. In Fig.\ref{figure:simul123_b} and Fig.\ref{figure:simul123_c}, the hot spot is in the middle-left and lower-left sub-square. In the heavily loaded hot spot simulations, when the number of users increases, the sum of the utility function decreases. In the moderately loaded hot spot simulations, the maximum sum of the utility function appears when the number of users is $441$. In Fig.\ref{figure:simul123_d}, the number of users is uniform in each sub-square. The maximum sum of the utility function appears when the number of users is $441$, too. We can observe that when the number of users is $441$, these APs are overloaded.

	\begin{figure}
		\begin{center}
			\begin{subfigure}[b]{0.4\textwidth}
				\includegraphics[width=6cm]{fig/simul_center.eps}
				\caption{center sub-square}
				\label{figure:simul123_a}
			\end{subfigure}
			\begin{subfigure}[b]{0.4\textwidth}
				\includegraphics[width=6cm]{fig/simul_middleleft.eps}
				\caption{middle-left sub-square}
				\label{figure:simul123_b}
			\end{subfigure}
			\begin{subfigure}[b]{0.4\textwidth}
				\includegraphics[width=6cm]{fig/simul_lowerleft.eps}
				\caption{lower-left sub-square}
				\label{figure:simul123_c}
			\end{subfigure}
			\begin{subfigure}[b]{0.4\textwidth}
				\includegraphics[width=6cm]{fig/simul_uniform.eps}
				\caption{uniform number}
				\label{figure:simul123_d}
			\end{subfigure}
			\caption{Comparison of sum of utility function of SIMUL1, 2, and 3.}
			\label{figure:simul123}
		\end{center}
	\end{figure}

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Introduction.tex
update

\section{Introduction}
	Wireless local area networks (WLANs) are widely used today. There are more and more users in WLANs because mobile devices (e.g., smartphones, tablets, etc.) become very popular in recent years. Users can connect to networks by associating their devices with access points (APs) pairwisely to upload and download data.

	In a WLAN, there is at least one AP to be deployed. On each AP, there are multiple channels to be set. The controller of each AP can select one among multiple channels to set it on the AP to communicate with users.

	We refer to a WLAN with the various bit rate as a multi-rate WLAN. The bit rate of each transmission link between the AP and the user may be different because the rate can be decided by Shannon-Hartley theorem according to the bandwidth of the channel and the signal-to-noise ratio (SNR). SNR is a function of the transmit power of the antenna on the AP, the distance between the AP and the user, and the noise in the environment. Therefore, when a user associates with different APs, the bit rate obtained by the user may be different.

	Multiple-input multiple-output (MIMO) is a method to improve the bit rate between the AP and the user by using the multiple spatial streams to transmit data on the same channel at the same time \cite{li2002mimo}. Twenty years ago, each AP or user almost has only one antenna to transmit or receive data. The controller of APs can only control the transmit power to adjust the bit rate of links between the AP and users. Next, someone finds out that if there are multiple antennas on APs and users, the AP can simultaneously transmit multiple spatial streams to a user on the same channel at the same time. It improves the sum-rate between the AP and the user. This method is called multiple-input multiple-output (MIMO).

	Multi-user MIMO allows an AP to transmit data to multiple users simultaneously on the same channel by using the method called beamforming. When an AP has multiple antennas, it can control the direction of the transmit signal by tunning the magnitude and the phase of the transmit signal at each antenna on the AP. Therefore, the AP can select one user and transmit data to it without interfering other users. This method not only increases the power gain but also decreases the interference to other users. We call this method beamforming.
	Because we can use beamforming to control the propagation direction of the transmit signal, we can make the directions of multiple transmit signals different such that they don't collide to each other. Then an AP with multiple antennas can transmit different signals to multiple users simultaneously. We call this environment  multi-user MIMO (MU-MIMO).

	The different decision of the AP association in enterprise WLANs will lead to the different result of the bandwidth allocation. The bandwidth here can be referred to as the average throughput during a time period. In order to allocate bandwidth to each user as much as possible, plenty of APs which belong to the same owner are deployed over a large population area like a campus, an enterprise, etc. This architecture is called an enterprise WLAN. There usually exist a central controller to manage all APs' setting in an enterprise WLAN. If the controller can make a good decision for AP association, it may be able to improve the bandwidth allocated to each user.

	Fairness should be considered in the AP association problem in addition to improving the bandwidth. Today there are two famous fairness type in the world. One is the max-min fairness, and the other is proportional fairness \cite{kelly1997charging}. In max-min fairness, the fairness criterion is that when we can't increase someone's allocated bandwidth if it results in decreasing another one's smaller allocated bandwidth, it is fair. In proportional fairness, when the allocated bandwidth $\{b_1^*,...,b_m^*\}$ is fair, for any other allocated bandwidth $ \{b_1,...,b_m\}$ will lead to $ \sum_{i=1}^{n} \frac{b_1-b_1^*}{b_1^*} \le 0 $. We maximize the allocated bandwidth of each user under the fairness constraint. According to references \cite{li2008proportional}, total allocated bandwidth of all users under the proportional fairness criterion is greater than that under the max-min fairness criterion.

	Therefore, we consider a problem about how to make an AP association for proportional fairness when there are multiple APs deployed in a multi-rate enterprise WLAN which supports MU-MIMO. If there are multiple antennas on each AP and on each user, then each user can receive from multiple antennas on the same AP at the same time. When we schedule the transmission time for the antenna on the AP, each time slot of the antenna can be assigned to only one user. So, if an AP is equipped with multiple antennas, the AP can be assigned to multiple users at the same time with different time slots of antennas. When each user is in the coverage areas of several APs, the user has many choices to select one AP among them to associate with. Therefore, we propose an algorithm for AP association for proportional fairness in an MU-MIMO multi-rate WLAN.

	%Because the channel state information will vary and a new user would like to make an association or an old user would like to leave, we will perform the AP association algorithm periodically.

	For convenience, the notations in the thesis are summarized in Table \ref{Tab:notation}.

	\begin{table} \small
		\centering \caption{Notations in the thesis.}
		\renewcommand\arraystretch{1.0}
		\begin{tabular}{|l|l|} % m{5.38cm}
			\hline	Symbol & Semantics \\
			\hline	$U$ & The set of users. \\
			\hline	$T$ & The set of antennas. \\
			\hline	$A$ & The set of APs. \\
			\hline	$T_i$ & The set of antennas on AP $i$. \\
			\hline	$U_i$ & The set of users associating with AP $i$. \\
			%	\hline	\(\omega_j\) & The priority of user \(j\). \\
			\hline	$b_j$ & The bandwidth allocated to user $j$. \\
			\hline	$r_{ikj}$ & The bit rate of the link between antenna $k$ on AP $i$ and user $j$. \\
			\hline	$r_{ij}$ & The bit rate of the link between antenna $i$ and user $j$. \\
			\hline	$t_{ikj}$ & The fractional time that user $j$ can receive from antenna $k$ on AP $i$. \\
			\hline	$p_{kj}$ & The fractional time that user $j$ can receive from antenna $k$ on the AP. \\
			\hline	$x_{ij}$ & User $j$ is associated to AP $i$ or not. \\
			\hline	$c_{j}$ & The number of antennas on user $j$. \\
			\hline
		\end{tabular}\label{Tab:notation}
	\end{table}

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/Related_Work.tex
update

% Related Work
\section{Related Work}
	We survey on the proportional fairness ,AP association problems, and MIMO.

	In \cite{kelly1997charging}, the motivation is to find how to set a price for the unit rate allocated to each USER in a SYSTEM consist of USERs and NETWORK such that for each USER, the utility function minus pay for allocated rate is maximum and the revenue of NETWORK is maximum. The famous contribution in this paper is the author proposes a proportional fairness criterion applied to the rate allocation and derive a utility function such that when the maximum of the sum of the utility function is attained, the rate allocation is in the proportional fairness condition.

	In \cite{li2008proportional}, the authors introduce a NP-hard problem called AP association for proportional fairness in multi-rate WLANs and propose two approximation algorithms. In simulations, they compare their results to another allocation for max-min fairness. The aggregate throughput of their algorithms is as much as 2.3 times more than that of the max-min fair allocation. The model in this paper is a kind of an integer model application in \cite{kelly1997charging}. The algorithm in this paper cannot be used for our problem AAPFM because we need to decide which user is assigned to which antennas on the AP with multiple antennas.

	In \cite{li2014ap}, the authors introduce the same problem as that in \cite{li2008proportional} and propose an approximation algorithm for AP association and a distributed heuristic algorithm to provide an AP selection criterion for newcomers.

	In \cite{baid2012network}, the authors consider a scenario as follows. There are several WLANs belong to different owners in an area. Each WLAN is composed of APs. The owner of a WLAN will set  different channel to each AP in this WLAN. However, APs in different WLANs may be set the same channel. If a user is covered by these APs, he may get interference. The authors propose an algorithm to cooperate APs in different WLANs in order to associate each user to only one AP in one WLAN and allocate the bandwidth to each user such that the bandwidth allocation is under proportional fairness. This paper seems like an extension of \cite{li2008proportional}.

	In \cite{karimi2014optimal}, the motivation is that because the number of channels is less than the number of APs in a WLAN, there will be multiple APs to be set the same channel when APs are deployed densely. APs using the same channel will interfere to each other, so they cannot transmit to users simultaneous when we perform time scheduling. Besides, if a user can associate with multiple APs, it may obtain more bandwidth. The authors propose an algorithm to select one channel to set for each AP, associate each user to one or multiple APs, and allocate bandwidth to each user such that bandwidth allocation is under proportional fairness.

	In \cite{gong2012ap}, the authors consider AP association problem in IEEE 802.11 WLANs. In the WLAN, clients associate with an AP with strongest signal strength automatically. However, it may lead to poor bandwidth allocation. Moreover, clients with different generations of IEEE 802.11 standard may be in the WLAN simultaneously. It will result in the upper bound of the data rate of each client may be different. The authors propose two AP association algorithms such that the bandwidth allocated to each client is proportional to the upper bound of the data rate of each client.

	In \cite{yoon2013probeam}, the authors propose an algorithm for joint client association and beam selection problem whose goal is to maximize the sum of the utility function of the allocated bandwidth by reusing the potential of beamforming in small-cell networks.

	In \cite{li2002mimo}, the authors establish an orthogonal frequency division multiplexing (OFDM) for MIMO channels (MIMO-OFDM) system to mitigate intersymbol interference and increase the transmission data rate.

	In \cite{aryafar2010design}, the authors design a practical multi-user beamforming system in WLANs and evaluate the performance of Zero Forcing Beamforming (ZFBF) algorithm \cite{yoo2006optimality}.

	In \cite{yoo2007multi}, the authors design a limited channel state information (CSI) feedback mechanism to mitigate the overhead of feedback by reducing the number of feedback bits.

	In \cite{xie2014scalable}, the authors proposed a distributed mechanism for selecting users to be served by an AP in MU-MIMO networks. An AP with $M$ antenna can transmit data to $M$ users at most in the downlink during each transmission interval. In order to reduce the overhead of CSI feedback but still keep the accuracy of CSI enough and maximize the total capacity of the AP, there are $M$ rounds in a transmission interval and in each round the mechanism selects one user that can increase the capacity to maximal.

%	\cite{arslan2007channel}\cite{blough2014interference}\cite{du2014ibeam}\cite{gong2012ap}\cite{kelly1997charging}\cite{li2002mimo}\cite{li2008proportional}\cite{li2014ap}\cite{wang2014simcast}\cite{xie2014scalable}\cite{yoo2007multi}\cite{yu2014combating}\cite{yoon2013probeam}\cite{aryafar2010design}\cite{yoo2006optimality}

### 2018-06-06 ap_association_for_proportional_fairness_in_mu-mimo_multi-rate_wlans/cthesis.tex
update

%!TEX encoding = UTF-8 Unicode 
\documentclass[a4paper,12pt]{report}
\usepackage{CJKutf8}
\usepackage{graphicx}
\usepackage[sf]{titlesec}

\topmargin 0cm \oddsidemargin 0.5in \headsep 1.5cm \headheight 0.5cm
\textheight 21.5cm \textwidth 15.2cm \marginparwidth 0cm
\marginparsep 0cm
\floatsep 0.8cm     %頁之上端與下端圖表與圖表之間的間距
\textfloatsep 0.8cm %頁之上端與下端圖表與文字之間的間距
\intextsep 1.0cm    %指定為 h 的圖表與文字之間的間距
%\jot 0cm       %Array 數式間的間距
%\abovedisplayskip 1.2cm    %數式的上端與其上面文章間的間距
%\belowdisplayskip 1.2cm    %數式的下端與其下面文章間的間距
%\abovedisplayshortskip 1.2cm   %數式的上端與其上面文章間的間距
%\belowdisplayshortskip 1.2cm   %數式的下端與其下面文章間的間距

\newtheorem{alg}{Algorithm}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{proof}{Proof}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{statement}{Statement}
\newtheorem{corollary}{Corollary}

\newcommand{\doublespace}
        {\addtolength{\baselineskip}{.6\baselineskip}}

\begin{document}

\begin{CJK}{UTF8}{bkai}

\titleformat{\chapter}[display]{\Huge}
            {第\ \thechapter\ 章}{0.2cm}{}
\renewcommand{\contentsname}{目錄}

%\setlength{\baselineskip}{22pt}

\begin{titlepage}
\begin{center}
{\fontsize{28}{28}國~  立~  清~  華~  大~  學}\\

\vspace{1.5cm}
\Huge{\underline{碩　士　論　文}}\\
\vspace{0.8cm}
%\Large{(草稿)}\\
\vspace{2.7cm} \Large{在多用戶多輸入多輸出的無線區域網路環境下，達成比例公平分配條件的無線網路基地台連接配對問題
}\\
\vspace{0.5cm} \Large{\bf AP Association for Proportional Fairness in MU-MIMO Multi-rate WLANs\\}

\vspace{3cm}
\parbox[t]{14cm}{
%實際寬度自行再調整
\doublespace{
{\bf 系　　別}：\underline{　資~訊~工~程~學~系　　~~}{\bf 組別}：\underline{　　　~~}\\
{\bf 學號姓名}：\underline{　102062650　陳~鈺~書（Yu-Shu~Chen）~~}\\
{\bf 指導教授}：\underline{　蔡~明~哲　博士~~（Dr.~Ming~Jer~Tsai）}\\
}}

\vspace{1cm}
中華民國一百零四年七月\\
\end{center}
\end{titlepage}

\cleardoublepage \pagenumbering{roman} \doublespace

\chapter*{中文摘要}
\addcontentsline{toc}{chapter}{中文摘要}

\indent
在無線區域網路裡無線網路基地台連接配對問題的演算法設計已經受到許多人的關注，這是因為分配給使用者的頻寬會隨著演算法的不同而有差異。為了要讓每個使用者所被分配到的頻寬能夠符合他的最低需求，在無線網路基地台連接配對問題需要去考慮公平性。已經存在的演算法只有考慮在每個無線網路基地台在某個時間點只能跟一個使用者溝通的環境下，去達到頻寬分配公平性最佳化的狀態。然後現在藉著使用波束成型技術可以讓有多根天線的無線網路基地台能夠同時跟多位使用者傳遞資料。

在這篇論文中，我們探討在多用戶多輸入多輸出的無線區域網路環境下，達成比例公平分配條件的無線網路基地台連接配對問題來使得分配給使用者頻寬的效用函數的和最大化。就我們所知，我們是第一個來探討這個問題的。在這篇論文中，我們會證明這是一個NP-hard 的問題並且提出一個近似演算法使得它的答案會不小於 $OPT - |U|\log(|A|)$，在這裡 $U$ 是使用者的集合，$A$ 是無線網路基地台的集合。

從模擬的結果可以看出我們所提出的演算法對於分配給使用者頻寬的效用函數的和有良好的表現。\\
~\\
\noindent
\\

\cleardoublepage

\end{CJK}

\end{document}

### 2018-06-06 paper.tex
update

\documentclass[a4paper,12pt]{report}

    \usepackage[english]{babel}
    \usepackage{graphicx}
    \linespread{1.5}
    \title{Implementation and Evaluation of Routing Algorithm in GENI Software-Defined Networking}
    \author{Wei-Hen Hsu}
    \date{\today}
    \begin{document}
    \begin{large}
    \maketitle{}
    \tableofcontents{}
    \chapter{Introduction}
    \qquad Software-defined networking (SDN) has received a lot of attention in recent years, 
            several routing algorithms have been proposed by researchers. The environment that evaluates a 
            routing algorithm is quite importmant.\par
    \qquad Commonly, building up a SDN environment with real OpenFlow switches for evaluating the porformance
            of routing algorithms is very persuasive. Unfortunately, a real OpenFlow switch is expensive. It's 
            costly to build a small-scale netwrok with real OpenFlow switches.\par
    \qquad Another tool for building the SDN environment is the network testbed. The network testbed is a 
            platform to provide network researchers with a realistic environment for testing. In some network testbeds, they are supported by governmentsit and it's free for researchers to use the testbed. Compared with previous ways, it is more cost-effective for researchers to build the environment.\par
    \qquad Therefore, in this thesis, we propsed a method to implement the routing algorithms in {\bf Global 
            Environment for Network Innovations (GENI)} SDN testbed. The routing algorithms fall into the following two main categories: (a) online routing algorithm; (b) offline routing algorithm. In each catergory, we describe the process of creating a SDN on GENI and implementing the rouing algorithm on SDN. 
    \chapter{General Background Information}
        \section{Software-defined networking}
        \qquad According to {\bf ONF(Open Networking Foundation)} definition of software-defined networking, SDN is 
                an architecture that is dynamic, manageable, cost-effective, and adaptable, making it ideal for the 
                high-bandwidth, dynamic nature of today’s applications. In traditional network, each network device 
                usually has its own control plane. The transport of the packet is processed by network device 
                individually. The SDN decouples the forwarding and control planes, removes the control plane from 
                network device and implements it in sofware instead. The SDN enables the control plane to beccome 
                directly programmable and the underlying infrastructure to be abstracted for applications and network 
                services. The OpenFlow® protocol is a foundational element for building SDN solutions.
        \section{OpenFlow}
        \qquad OpenFlow is a communications protocol between SDN controller and OpenFlow switch that enables the SDN 
                controller to direct interact with the forwarding plane of network devices such as switches and 
                routers. Figure 2.1 shows the main components of an OpenFlow switch.
        \begin{figure}[hb]
          \caption{Main components of an OpenFlow switch.}
          \centering
            \includegraphics[width=0.5\textwidth]{OpenFlow.png}
        \end{figure}
        \subsection{OpenFlow switch components}
        \qquad An OpenFlow switch consists one or more flow tables, which perform packet lookups and forwarding. The controller could use the OpenFlow protocol to add, update, and delete flow entries in flow tables. In each flow table, it contains a set of flow entries; each flow entry consists of match fields, counters, and a set of instructions to apply to matching packets. (see Table 2.1)\\
        \begin{table}
          \centering
          \begin{tabular}[c]{|l|l|l|l|l|l|}
          \hline
          Match Fields & Priority & Counter & Instructions & Timeouts & Cookie \\
          \hline
          \end{tabular}
          \caption{Main components of a flow entry in a flow table}
        \end{table}
      \section{GENI}
      \qquad GENI provides a virtual laboratory for networking and 		 distributed systems research and education.Researcher could obtain compute resources from locations around the United States. Figure 2.2 show the map of GENI compute and netwrok resouces. GENI allows user to install custom software or even custom operating systems on compute resources. Furthermore, researcher could control how network switches in their experiment handle traffic flows. GENI is sponsored by the U.S. National Science Foundation (NSF). If the researchers' institution belongs to an identity federation, the researchers are able to log in using their usual username and password. If their institution does not belong, they could apply for an account at the NCSA identity Provider.
      \begin{figure}[h]
          \caption{The map of GENI compute and netwrok resouces.}
          \centering
            \includegraphics[width=1.0\textwidth]{GENI-MAP.jpg}
      \end{figure}
     \section{Open vSwitch}
     \section{Ryu controller}
     \qquad Ryu is a component-based SDN framework. Ryu is fully written in Python and provides software components with well defined API that make it easy for developers to create new management and control applications. Figures 2.3 shows the model of Ryu application. The data path thread will collect all the events from OpenFlow switch and dispatch the events to the event handler to process it. The programmer should define the event handler how to process the event. Figure 2.4 shows the status of ryu from the beginning till the end.  
     \begin{figure}
          \caption{Ryu application programming model.}
          \centering
            \includegraphics[width=1.0\textwidth]{ryu_model.png}
          \caption{The four status in ryu controller}
          	\includegraphics[width=1.0\textwidth]{ryu_graph.png}
      	\end{figure}
  \chapter{System model}
     \section{GENI model}
  \chapter{Implementation of Routing Algorithm in GENI}
  	\section{The reservation of compute resources for customized topology}
		\qquad In GENI, There are three methods to reserve the resources: (a) setting the topology manually; (b) choose existing topology; (c) import Resouce spectification (Rspec) documents. Figure 4.1 to Figure 4.3 show the three methdos to reserve the resources. In (a), you could just drag the components into the screen and create the topology you desire. In (b) choosing the existing topology that the geni offering. In (c) To use the Rspec documents, you could write a program to output the Rspec document by following the Rspec structure.
		\begin{figure}
          \caption{(a) Setting the topology manually.}
          \centering
            \includegraphics[width=1.0\textwidth]{geni_manual.png}
          \caption{(b) Choose existing topology.}
            \includegraphics[width=1.0\textwidth]{choose_existing.png}
          \caption{(c) Import Resouce spectification (Rspec) documents.}
            \includegraphics[width=1.0\textwidth]{rspec_format.png}
      	\end{figure}
   \section{Offline algorithm}
     \subsection{create the network graph for the input of routing algorithm}
     \qquad After reserve the resources, copy the network structure document from GENI online website. Fugure 4.4 shows the the network structure document. The network structure document contains the information of nodes and links. Using this document to create the netowrk graph for the input of the routing algorithm.
     \begin{figure}
        \caption{The network structure in GENI}
        \centering
          \includegraphics[width=1.0\textwidth]{Raw_resource.png}
     \end{figure}
     \subsection{setting up the demands}
     \qquad After the routing algorithm compute the pathes of the demands. In order to let the Open vSwitch to identify each demands, we use ip of source, ip of destination, port of destination to identify each demands.
 For each nodes, we create a script to run the demands with given information. 
 	\subsection{setting up the controller}
 	\qquad For controller, we create a dictionary for it. Every time when a node asks the controller how to process the demands, controller could use ip of source, ip of destination, port of destination as a key to find the path of the demand then send the OpenFlow message to the switch for adding the flow into the flow table. 
 	\section{Online algorithm}
 		\subsection{ryu controller}
 		\qquad In ryu controller, we need to implement a topology discovery which the routing algorithm could use. Figure 4.5 is the package which the Ryu controller need to import. Figure 4.6 is the code to discover topology.
 		\begin{figure}
          \caption{Ryu controller import package for topology discovery.}
          \centering
            \includegraphics[width=1.0\textwidth]{ryu_import.png}
          \caption{The code of topology discovery in Ryu controller.}
            \includegraphics[width=1.0\textwidth]{ryu_discovery.png}
      	\end{figure}
     \end{large}
    \end{document}

### 2018-06-06 template.tex
update

\documentclass[conference]{IEEEtran}

\usepackage[linesnumbered, ruled]{algorithm2e}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem*{example*}{Example}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}

\usepackage{siunitx}
%\usepackage[square,numbers]{natbib}
\usepackage{graphicx}
\usepackage{mathrsfs}
\usepackage[caption=false]{subfig}
\usepackage{cite}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\columnsep 0.21in
\begin{document}

\title{This is Title}

\author{
	\IEEEauthorblockN{Shu-Yen Hou\IEEEauthorrefmark{1},
		and Ming-Jer Tsai\IEEEauthorrefmark{1}
	}
	\IEEEauthorblockA{
		\IEEEauthorrefmark{1}Department of Computer Science, National Tsing Hua University, Hsinchu, Taiwan, ROC \\
		lazyeagles@gmail.com, itriA00550@itri.org.tw, g9962515@cs.nthu.edu.tw, mjtsai@cs.nthu.edu.tw
	}
}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
abstract...	
\end{abstract}

% no keywords

\section{Introduction}
...

\section{Preliminary}
...

\subsection{The Routing Protocol}\label{subsec:RPL}
...

\subsection{The MAC Protocol}\label{subsec:TSCH}
..

\subsection{The Scheduling Approach}\label{subsec:DeTAS}
..

\subsection{The Data Delivery Probability}\label{subsec:data delivery probability}
..

\section{The Problem}

\subsection{The Scenario and Network Model}\label{subsec:scenario}
\subsubsection{The Scenario}
In the smart grid, there are two methods to connect user's meters to transmit the informations of electric using to the power company. One is a wireless network and the other is a wired network. For the wireless network, we use Radio Frequency (RF) sensors to connect. And for the wired network, we use Power Line Communications (PLC) sensors to connect. 
\par For each meter be covered by a wired or wireless sensor, it means the informations of the meter can be transmitted to the power company by the wired or the wireless sensor, which covers it.	
\par If we only use the wired network to connect user's meters to transmit to the power company, here comes some questions. First, because PLC sensors are wired sensors, the number of meters by one PLC can cover are limited. It means it needs to take a lot of PLCs to cover all user's meters. Second, because of the previous question, it need to take a lots human resources to place the PLCs. Based on the above, it need much more cost, if we only use the wired network to cover all user's meters. 
\par On the other hand, if we only use the wireless network to cover all user's meters. It also comes some questions. In the wireless network, there are links between the RFs and meters, each link has probability, which means the sccessful rate of transmit informations from the meter to the RF. The informations of meters can be transmited successful by the RFs depends on value of the probability of the RF. Even there are links between meters and RFs, it is still possible that the value of probabilities are too low to transmit informations to the RF successfully. And the quality of the network transmission also is the topic which needs to satisfy. Because of the previous question, we can't only use wireless networks in our problem. Obviously, it needs both wired networks and wireless networks to transmit the informations of user's meters to the power company in the smart grid. 
\par But how to place the PLCs and the RFs in low cost, which means the number of the PLCs and the RFs is as few as possible, and also needs in the certain quality, it is what our problem is.

\subsection{The Problem and Hardness}\label{subsec:problem}
...
\begin{definition}\label{def:msplrg}
	Problem definition...
\end{definition}

\begin{theorem}\label{thm:np-hard}
	...
\end{theorem}
\begin{proof}
	...
\end{proof}

\section{The Proposed Algorithm}

\subsection{The Cluster Construction}\label{subsec: cluster construction}
...

\subsection{The Sink Selection}\label{subsec: cluster selection}
...

\subsection{The DODAG Establishment}\label{subsec: cluster prune}
...

\section{Simulations}

\subsection{Simulation Setup}

\textbf{Network instances:}

\textbf{Comparison methods and performance metrics:}

\subsection{Simulation Results}

\textbf{The number of selected concentrators and assigned channels:}

\textbf{The minimum and maximum sizes of the DODAGs:}

\section{Conclusion}
...

\bibliographystyle{IEEEtran}
%\bibliography{references}

% that's all folks
\end{document}

### 2018-06-06 paper.tex
update openvswitch

@@
      \section{Open vSwitch}
+     \qquad Open vSwitch is a open source, multi layer virtual switch implemented in software.
+It can be intergrated with hardware where it can act as as control plane.
+One example is it can handle OnpenFlow control plane in a hardware silicon.
+There are three mainly components in Open vSwitch: (a) Control Plane; (b) Kernel Mode; (c) Command line interface.
      \section{Ryu controller}

### 2018-06-07 paper.tex
update a lot

@@
 Ryu is fully written in Python and provides software components with well defined API that make it easy for developers to create new management and control applications.
-Figures 2.3 shows the model of Ryu application.
+  \chapter{System model}
+     \section{Workflow of GENI}
+     \qquad Figure 3.1 shows the workflow of GENI.
+In the beginning, the GENI experimenters need to creat a slice.
+A GENI slice is: (a) The unit of isolation for experiments.
+Only experimenters who are members of a slice can make changes to experiments in that slice; (b) A container for resources used in an experiment.
+     \newline
+     \null\qquad For creating a specific topology, there are three methods to achieve that.
+Resouece Specification (RSpec) is a XML document in a prescribed format.
+Experimenters sned to  aggregates a request RSpec that describe the rosources they want.\
+     \newline
+     \null\qquad After finishing in reservation, experimenters could use GENI desktop tool to configure each node manually.
+Another method is to use the manifest RSpec, manifest RSpec describes the roesources the got.
+The manifest include the names and IP addresses and login accounts of compute resources.
+The experimenters could use SSH to login in the resources and configure the nodes.
+     \newline
+     \null\qquad When finished setting the nodes including controller, the experimenters use SSH to connect to each node and run the {\bf iPerf} to start the traffic.
+{\bf iPerf} is a software that could create the traffic in the networks.
+     \newline
+     \null\qquad Finally, the experiments could clone the mesaurment datas from each node and view the information they want.
+       \begin{figure}
+          \caption{The workflow of GENI.}
+          \centering
+          \includegraphics[width=1.0\textwidth]{geni_workflow.png}
+       \end{figure}
+    \section{Network in GENI}
+      \qquad Figure 3.2 shows the network in GENI. Each nodes is a virtual machine installed the Open vSwitch. The controller is installed the RYU controller.
+    \begin{figure}
+          \caption{The network in GENI.}
+          \centering
+          \includegraphics[width=1.0\textwidth]{GENI_network.png}
+       \end{figure}
+    \section{Ryu controller}
+    \qquad In Ryu controller, the controller will make connection to each switch by using OpenFlow protocol to send the hello message.
+After receving the reply message, the controller will want to get the information of switches.
+The controller will send the features request to the switch and wait the reply message.
+Then, the controller will send to flow mod message to the switch which setting the switch how to handle the packet.
+After that, the controller will start to listen the packet.
+When a packet is sent to the controller by the switch.
+The controller will create an event.
+Because the event is casue by a pcket being sent, so the evnet will be sent to the function which handle with the packet in controller.Figures 3.3 shows the model of Ryu application.
 The data path thread will collect all the events from OpenFlow switch and dispatch the events to the event handler to process it.
 The programmer should define the event handler how to process the event.
-Figure 2.4 shows the status of ryu from the beginning till the end.
-     \begin{figure}
+Figure 3.4 shows the status of ryu from the beginning till the end.
+Figure 3.5 is a example code of how the controller handling the packet.
+     \begin{figure}[p]
           \caption{Ryu application programming model.}
@@
           	\includegraphics[width=1.0\textwidth]{ryu_graph.png}
+
       	\end{figure}
-  \chapter{System model}
-     \section{GENI model}
+     \begin{figure}[p]
+          \centering
+          \caption{The example of the function which handle the packet}
+          	\includegraphics[width=1.0\textwidth]{packet_in_handler.png}
+      	\end{figure}
   \chapter{Implementation of Routing Algorithm in GENI}
@@
       	\end{figure}
+  \chapter{Case study}
+  \chapter{Experiment results}
+  \chapter{Summary}
+    \section{conclusion}
+    \section{future work}
+  \chapter{References}
      \end{large}

### 2018-06-11 paper.tex
update

@@
 \documentclass[a4paper,12pt]{report}
-
   \usepackage[english]{babel}
@@
     \section{OpenFlow}
-        \qquad OpenFlow is a communications protocol between SDN controller and OpenFlow switch that enables the SDN 
+      \qquad OpenFlow is a communication protocol between SDN controller and OpenFlow switch that enables the SDN 
                 controller to direct interact with the forwarding plane of network devices such as switches and 
@@
 	     \subsection{create the network graph for the input of routing algorithm}
-     \qquad After reserve the resources, copy the network structure document from GENI online website.
+	     \qquad After reserving the resources, copy the network structure document from GENI online website.
 Fugure 4.4 shows the the network structure document.
@@
 Figure 4.6 is the code to discover topology.
+After the controller gets the topology, every time when a packet sends to the controller, we parse the information of the packet.
+Getting its ip source, ip destination, destination port as the demand's key.
+Input this key and topology into the algorithm then get the path output by controller.
+Sending the messages to the switch to add the flow in the flow table.
 	 		\begin{figure}
@@
   \chapter{Case study}
+  \section{Maximum Concurrent Flow Problem in MPLS-based Software Defined Networks}
+    \qquad In this section, we study the Maximum Concurrent Flow Problem in MPLS-based Software Defined Networks and implement four algorithms in GENI.
+Because the MPLS is a per-flow routing, the number of flow paths through a node (switch) needs to be bounded due to the limited ternary content addressable memory (TCAM).
+Therefore, the problem term to be bounded path-degree maximum concurrent flow problem (BPMCF)
+    \subsection{Problem definition}
+    \qquad Given a network topology G = (V, E) with link link capacity (bandwidth capacity) 
   \chapter{Experiment results}

### 2018-06-11 paper.tex
update

@@
      \null\qquad When finished setting the nodes including controller, the experimenters use SSH to connect to each node and run the {\bf iPerf} to start the traffic.
-{\bf iPerf} is a software that could create the traffic in the networks.
+{\bf iPerf} is a software that could create the traffic in the networks \cite{iperf}.
      \newline
@@
 Because the MPLS is a per-flow routing, the number of flow paths through a node (switch) needs to be bounded due to the limited ternary content addressable memory (TCAM).
-Therefore, the problem term to be bounded path-degree maximum concurrent flow problem (BPMCF)
+Therefore, the problem term to be bounded forwarding rule maximum concurrent flow problem (BFRMCF)
     \subsection{Problem definition}
-    \qquad Given a network topology G = (V, E) with link link capacity (bandwidth capacity) 
+    \qquad Given a network topology $G=(V, E)$ with link link capacity (bandwidth capacity) $c_e\in R^+$ associated with each directed link $e\in E$ and node capacity (forwarding table size) $b_v\in Z^+$ associated with each node (SDN-FE) $v\in V$, and given a set of flows $F=\{ 1, 2, ..., |F|\}$.
+Each flow $f\in F$ is associated with a source-destination pair $ \left( s_f,t_f \right)\subseteq V \times V $ and the transmission demand $d_f \in R^+$.
+The Bounded Forwarding Rules Maximum Concurrent Flow Problem (BFRMCF) asks for the forwarding paths and the transmission rate on each chosen path such that 1) for each flow $f$, the rate is at least $\lambda d_f$, \newline 2) for each flow $f$, the rate is at most $d_f$ (the demand constraints), \newline 3) for each link $e$, the taotal rate through $e$ are at most $c_e$ (the link capacity constraints), \newline 4) for each node $v$, the number of flow paths going through $v$ does not exceed $b_v$ (the node capacity constraints), and \newline 5) $\lambda$ is maxized.
+\newline\null
+\qquad Let $P_f$ be the set of possible forwarding paths for flow $f$ in the network, and $P=P_1 \cup P_2 \cup ...
+\cup P_F$.
+Moreover, let $c_p$ be the capacity of a path $p \in P_f$, i.e., $c_p = min\{ min_{e:e\in p} \{ c_e \}, d_f\}$.
+In addition, variable $x\left( p \right)$ deontes the fraction of the transmission rate on path $p$ to $c_p$, and variable $y\left( p \right) = 1$ if and only if $p$ is a chosen forwarding path.
+The BFRMCF problem is formulated as an integer linear program as below.
+			\begin{figure}
+	          \centering
+	            \includegraphics[width=1.0\textwidth]{it_program.png}
+	      	\end{figure}
+\section{Algorithms of BFRMCF}
+\qquad We reivew three offline algorithms for BFRMCF problem. In \cite{our}, \cite{grag}, \cite{gk}, we implement it on GENI and show the total throughput and the $\lambda$ in rxperiment results.
+\section{Implement method}
+\subsection{ The ryu controller}
+  \qquad In ryu controller we need to parse the packet to get the source of ip, destination of ip and destination of port for pretending as a key. Figure 5.1 is the code in ryu for parsing the packet.
+  \begin{figure}[b]
+	          \caption{The code of parse packet}
+	          \centering
+	            \includegraphics[width=1.0\textwidth]{ryu_controller_parse.png}
+	      	\end{figure}
+\subsection{ OpenFlw version and flow table size}	
+\qquad In BFRMCF problem, because it has path degree constraint, we need to let the Open vSwitch support to 1.3 version and set up the flow limit. Figure 5.2, 5.3 is the code to set up. 
+			\begin{figure}[b]
+	          \caption{Support to OpenFlow 1.3}
+	          \centering
+	            \includegraphics[width=1.0\textwidth]{openflow1_3.png}
+	          \caption{Change flow table size}
+	            \includegraphics[width=1.0\textwidth]{flow_table.png}
+	          \caption{The code of iPerf}
+	          \centering
+	            \includegraphics[width=1.0\textwidth]{iperf.png}
+	      	\end{figure}
+\subsection{iPerf}
+	\qquad For setting a target bandwidth, because TCP couldn't fixed in a target bandwidth, so we selected UDP to transport.
+In figure 5.4, for server side, we user -p parameter to set up the server in a particular listen port, -u let the server listen for UDP packet.
+	\newline\null\qquad For a client side, -c menas to be a client, -b is to set a target bandwidth. -p is transport to a particular listen port.
   \chapter{Experiment results}
+  \qquad We tested three algorithms which are Garg’s algorithm \cite{grag}, Gushchin’s algorithm \cite{gk} and PD's algorithm \cite{our}.The network instances were obtained from the 6 real-life traces from SNDlib \cite{SNDlib}.
+Since the capacity of each node is unavailable, we set the switch capacity from the 0.1 number of demands($|K|$) to $1.0|K|$.
+The following figures show the  minimum fraction and total throughput in different topologys.
+  \begin{figure}[ht]
+    \caption{The impact of the switch capacity on the minimum fraction on GENI.}
+	\centering
+	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
+	  \includegraphics[width=1.0\textwidth]{abilene_geni_lambda_e05.eps}
+	  \includegraphics[width=1.0\textwidth]{newyork_geni_lambda_e05.eps}
+  \end{figure}
+    \begin{figure}[ht]
+    \caption{The impact of the switch capacity on the minimum fraction on GENI.}
+	\centering
+	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
+	  \includegraphics[width=1.0\textwidth]{polska_geni_lambda_e05.eps}
+	  \includegraphics[width=1.0\textwidth]{di-yuan_geni_lambda_e05.eps}
+  \end{figure}
+  \begin{figure}[ht]
+    \caption{The impact of the switch capacity on the minimum fraction on GENI.}
+	\centering
+	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
+	  \includegraphics[width=1.0\textwidth]{nobel-us_geni_lambda_e05.eps}
+	  \includegraphics[width=1.0\textwidth]{pdh_geni_lambda_e05.eps}
+  \end{figure}
+
+    \begin{figure}[ht]
+    \caption{The impact of the switch capacity on the total throughput on GENI.}
+	\centering
+	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
+	  \includegraphics[width=1.0\textwidth]{abilene_geni_throughput_e05.eps}
+	  \includegraphics[width=1.0\textwidth]{newyork_geni_throughput_e05.eps}
+  \end{figure}
+    \begin{figure}[ht]
+    \caption{The impact of the switch capacity on the total throughput on GENI.}
+	\centering
+	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
+	  \includegraphics[width=1.0\textwidth]{polska_geni_throughput_e05.eps}
+	  \includegraphics[width=1.0\textwidth]{di-yuan_geni_throughput_e05.eps}
+  \end{figure}
+  \begin{figure}[ht]
+    \caption{The impact of the switch capacity on the total throughput on GENI.}
+	\centering
+	  \includegraphics[width=1.0\textwidth]{lambda_legend.eps}
+	  \includegraphics[width=1.0\textwidth]{nobel-us_geni_throughput_e05.eps}
+	  \includegraphics[width=1.0\textwidth]{pdh_geni_throughput_e05.eps}
+  \end{figure}
   \chapter{Summary}
@@
     \section{future work}
-  \chapter{References}
+  \begin{thebibliography}{1}
+\bibitem{iperf}
+    iPerf, \emph{https://iperf.fr/}.
+\bibitem{our}
+    Tzu-Wen Chang, Yao-Jen Tang, Ming-Jer Tsai, \emph{Efficient Algorithm for Maximum Concurrent Flow Problem in MPLS-based Software Defined Networks}.
+
+\bibitem{grag}
+    N. Garg and J. Könemann. \emph{“Faster and simpler algorithms for multicom-modity flow and other fractional packing problems,”} SIAM Journal on
+Computing, 2007.
+\bibitem{gk}
+	A. Gushchin, A. Walid, and A. Tang, “Enabling service function chaining
+through routing optimization in software defined networks,” in IEEE
+Allerton Conference on Communication, Control, and Computing, 2015.
+\bibitem{SNDlib}
+	S. Orlowski, R. Wessäly, M. Pióro, and A. Tomaszewski, “Sndlib 1.0-
+survivable network design library,” Networks, 2010. [Online]. Available:
+http://sndlib.zib.de
+\end{thebibliography}
   \end{large}

### 2018-06-11 paper.tex
update

@@
     \section{conclusion}
-    \section{future work}
+    \qquad For implementing a routing algorithm of SDN, GENI is a persuasive environment for experiment compared to simulator like NS-2, mininet, ...
+.
+In this thesis, we divided the algorithms into online algorithm and offline algorithm.
+For each part, we gave a full description about how to implement it in GENI.
+Reader could base on this thesis to get a faster way for building their experiment.
   \begin{thebibliography}{1}

### 2018-06-12 paper.tex
update

@@
 \documentclass[a4paper,12pt]{report}
+  \usepackage{CJKutf8}
   \usepackage[english]{babel}
   \usepackage{graphicx}
+  \usepackage[sf]{titlesec}
+  \topmargin 0cm \oddsidemargin 0.5in \headsep 1.5cm \headheight 0.5cm
+\textheight 21.5cm \textwidth 15.2cm \marginparwidth 0cm
+\marginparsep 0cm
   \linespread{1.5}
-  \title{Implementation and Evaluation of Routing Algorithm in GENI Software-Defined Networking}
-  \author{Wei-Hen Hsu}
-  \date{\today}
+  %\title{Implementation and Evaluation of Routing Algorithm in GENI Software-Defined Networking}
+  %\author{Wei-Hen Hsu}
+  %\date{\today}
   \begin{document}
+  \begin{CJK*}{UTF8}{bkai}
+
+  \begin{titlepage}
+  \begin{center}
+  {\fontsize{28}{28}國~  立~  清~  華~  大~  學}\\
+
+\vspace{1.5cm}
+\Huge{\underline{碩　士　論　文}}\\
+\vspace{0.8cm}
+%\Large{(草稿)}\\
+\vspace{2.4cm} \Large{在GENI環境裡﹐將路由演算法實做進軟體定義網路裡並且評估其效能
+}\\
+\vspace{0.5cm} \Large{\bf Implementation and Evaluation of Routing Algorithm in GENI with Software-Defined Networking\\}
+\vspace{2cm}
+\parbox[t]{14cm}{
+{\bf 系　　別}：\underline{　資~訊~工~程~學~系　　~~}{\bf 組別}：\underline{　　　~~}\\
+{\bf 學號姓名}：\underline{　105062598　徐~偉~涵（Wei-Hen~Hsu）~~}\\
+{\bf 指導教授}：\underline{　蔡~明~哲　博士~~（Dr.~Ming~Jer~Tsai）}\\
+}
+\vspace{0cm}
+中華民國一百零四年七月\\
+\clearpage
+  \end{center}
+  \end{titlepage}
+
+  \chapter*{中文摘要}
+  \pagenumbering{Roman}
+  \addcontentsline{toc}{chapter}{中文摘要}
+  \qquad 軟體定義網路越來越受到重視, 而許多的路由演算法相繼被提出, 評測演算法的表現能力成了重要的議題.
+以實體的交換機搭建出的軟體定義網路環境雖然真實, 但所需的成本極大.
+實驗床是另一種搭建軟體定義網路環境的方法, 實驗床大部分是由某些組織或者企業所搭建出來的環境, 它提供給研究者搭建環境時所需要的計算及網路資源, 並且提供界面讓研究者可以在上面操作設定其所需的實驗環境, 因為所使用的資源是跟許多人共享使用的, 所以成本相較於實體交換機少很多, 而所量測出的實驗數據又比依靠軟體模擬可信許多.
+\newline\null\qquad 因此本論文中, 探討如何在一個GENI實驗床中建立出一個軟體定義網路, 並且我們將路由演算法區分為線下與線上的演算法, 針對這兩種演算法, 我們逐一探討如何將其放入所搭建好的軟體定義網路環境中並且進行測試與收集研究者所需要的測試結果.
+  \clearpage
+  \chapter*{Abstract}
+  \addcontentsline{toc}{chapter}{Abstract}
+  \qquad Software-Defined networking has received more and more attentation recently, lots of routing algorithms have been proposed.
+For evaluating the performace of a routing algorithm becomes a important issue.
+Although Using real OpenFlow switch for constructing a software-defined networking is quite real, the cost for building is vrey high.
+The network testbed is another way for build software-defined networking.
+The network testbed is usually created by some organizations or enterprises.
+It offers the compute and network resources for the researchers.
+Also, it offers a platform for the researchers to operate and build the experimental environment they wnat.
+Because the compute and network resources are shared by other researchers, the cost is lower compared to building by real machines.
+Also, the result of the experiment is more persuasive than testing by some simulators.
   \begin{large}
-  \maketitle{}
+  \addcontentsline{toc}{chapter}{Contents}
   \tableofcontents{}
   \chapter{Introduction}
+  \setcounter{page}{1}
+  \pagenumbering{arabic}
 	    \qquad Software-defined networking (SDN) has received a lot of attention in recent years, 
@@
     \section{Software-defined networking}
-      \qquad According to {\bf ONF(Open Networking Foundation)} definition of software-defined networking, SDN is 
+      \qquad According to {\bf ONF(Open Networking Foundation)} \cite{ONF} definition of software-defined networking, SDN is 
                 an architecture that is dynamic, manageable, cost-effective, and adaptable, making it ideal for the 
@@
                 individually. The SDN decouples the forwarding and control planes, removes the control plane from 
-                network device and implements it in sofware instead. The SDN enables the control plane to beccome 
+                network device and implements it in sofware instead. In Figure 2.1, (a) is the traditional network and (b) is SDN. The SDN enables the control plane to beccome 
                 directly programmable and the underlying infrastructure to be abstracted for applications and network 
                 services. The OpenFlow® protocol is a foundational element for building SDN solutions.
+    \begin{figure}
+          \caption{Traditional network and SDN.}
+          \centering
+            \includegraphics[width=1.0\textwidth]{tra_sdn.png}
+        \end{figure}
     \section{OpenFlow}
@@
                 controller to direct interact with the forwarding plane of network devices such as switches and 
-                routers. Figure 2.1 shows the main components of an OpenFlow switch.
+                routers. Figure 2.2 shows the main components of an OpenFlow switch.
         \begin{figure}[hb]
@@
       \section{GENI}
-      \qquad GENI provides a virtual laboratory for networking and 		 distributed systems research and education.Researcher could obtain compute resources from locations around the United States.
-Figure 2.2 show the map of GENI compute and netwrok resouces.
+      \qquad GENI \cite{GENI} provides a virtual laboratory for networking and 		 distributed systems research and education.Researcher could obtain compute resources from locations around the United States.
+Figure 2.3 shows the map of GENI compute and netwrok resouces.
 GENI allows user to install custom software or even custom operating systems on compute resources.
@@
 National Science Foundation (NSF).
-If the researchers' institution belongs to an identity federation, the researchers are able to log in using their usual username and password.
+If the researchers' institution belongs to an identity federation, the researchers are able to login using their usual username and password.
 If their institution does not belong, they could apply for an account at the NCSA identity Provider.
@@
      \section{Open vSwitch}
-     \qquad Open vSwitch is a open source, multi layer virtual switch implemented in software.
+     \qquad Open vSwitch \cite{openvswitch} is a open source, multi layer virtual switch implemented in software.
 It can be intergrated with hardware where it can act as as control plane.
@@
      \qquad Figure 3.1 shows the workflow of GENI.
-In the beginning, the GENI experimenters need to creat a slice.
+     \subsection{Create a slice}
+     \qquad In the beginning, the GENI experimenters need to creat a slice.
 A GENI slice is: (a) The unit of isolation for experiments.
 Only experimenters who are members of a slice can make changes to experiments in that slice; (b) A container for resources used in an experiment.
-     \newline
-     \null\qquad For creating a specific topology, there are three methods to achieve that.
+     \subsection{Create a topology}
+     \qquad For creating a specific topology, there are three methods to achieve that.
 Resouece Specification (RSpec) is a XML document in a prescribed format.
-Experimenters sned to  aggregates a request RSpec that describe the rosources they want.\
-     \newline
-     \null\qquad After finishing in reservation, experimenters could use GENI desktop tool to configure each node manually.
+Experimenters sned to  aggregates a request RSpec that describe the rosources they want.
+     \subsection{Configure switches and controller}
+     \qquad After finishing in reservation, experimenters could use GENI desktop tool to configure each node manually.
 Another method is to use the manifest RSpec, manifest RSpec describes the roesources the got.
@@
 The experimenters could use SSH to login in the resources and configure the nodes.
+     \subsection{Run the experiment and collect the data}
+     \qquad When finished setting the nodes including controller, the experimenters use SSH to connect to each node and run the {\bf iPerf} to start the traffic.
+{\bf iPerf}  \cite{iperf} is a software that could create the traffic in the networks.
      \newline
-     \null\qquad When finished setting the nodes including controller, the experimenters use SSH to connect to each node and run the {\bf iPerf} to start the traffic.
-{\bf iPerf} is a software that could create the traffic in the networks \cite{iperf}.
-     \newline
-     \null\qquad Finally, the experiments could clone the mesaurment datas from each node and view the information they want.
+     \null\qquad Finally, the experiments could clone the mesaurment data from each node and view the information they want.
        \begin{figure}
@@
 	            \includegraphics[width=1.0\textwidth]{choose_existing.png}
+	      	\end{figure}
+	      	\begin{figure}	         
+	          \centering
 	          \caption{(c) Import Resouce spectification (Rspec) documents.}
@@
   \end{figure}
-  \chapter{Summary}
-    \section{conclusion}
+  \chapter{Conclusion}
     \qquad For implementing a routing algorithm of SDN, GENI is a persuasive environment for experiment compared to simulator like NS-2, mininet, ...
@@
 Reader could base on this thesis to get a faster way for building their experiment.
+ \cleardoublepage
   \begin{thebibliography}{1}
+%\phantomsection
+\addcontentsline{toc}{chapter}{Bibliography} 
+\bibitem{ONF}
+    Open-Network-Foundation, https://www.opennetworking.org/.
+\bibitem{GENI}
+    GENI, http://www.geni.net/.
+\bibitem{openvswitch}
+    Open vSwitch, https://www.openvswitch.org/.
 \bibitem{iperf}
@@
   \end{large}
+  \end{CJK*}
   \end{document}
